### 2022-05-08 paper/Paper.tex
period

\documentclass[11pt,titlepage]{article}
\usepackage{TCSToolkit}

\newcommand{\dofloor}[1]{\lfloor#1\rfloor}
\newcommand{\doceil}[1]{\lceil#1\rceil}

%%%%% Stuff you can change %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\myname}{Lev Stambler}
%

%% Custom Commands
\newcommand{\rationalPeriod}{{T^j}'}
\newcommand{\statePeriod}{T^j}
\newcommand{\seedAngle}[1]{{\theta_{#1}}^j}
\newcommand{\seedAngleNotime}{{\theta}^j}
\newcommand{\state}[2]{{s_{#1}}^{#2}}
\newcommand{\stateNotime}[1]{s^{#1}}
\newcommand{\totalPeriod}{T}

%
% Final tip: you can reference HW5 in your TeX using \Cref{hw:5}; 
% and, you can reference HW5.Problem3 in your TeX using \Cref{prob:5.3}
%

%%%%% Section-renaming code by egreg
\makeatletter
% we use \prefix@<level> only if it is defined
\renewcommand{\@seccntformat}[1]{%
  \ifcsname prefix@#1\endcsname
    \csname prefix@#1\endcsname
  \else
    \csname the#1\endcsname\quad
  \fi}
% Now we define our homework section prefixes
% \newcommand\prefix@section{Homework \thesection: }
% \newcommand{\prefix@subsection}{Problem \thesubsection: }
% \newcommand{\prefix@subsubsection}{Section \thesubsubsection: }
\makeatother
%%%%%

\begin{document}

\title{Drawing Math}

\author{\myname}

\date{\today}

\maketitle

\pagebreak
\section{Introduction}
- Numberphile video
- I was bored and this looked fun
- I wasn't paying attention in one of my lectures...
- This paper is purely for funs... for now

\section{Background}
- Digital math
- Euler's formula
- I payed attention in some of my lectures

\section{Definitions and questions}
\subsection{Definitions}
Say you (yes you!) had a turtle living in $D$ dimensional Euclidean
space and in discrete time. At time step $i$, where $i \in \Z$ and $i > 0$,
the turtle has position $p_i \in \R^D$.
Then, lets define $\Delta p_{i+1} = p_{i+1} - p_i$; in other words, $\Delta p_{i+1}$ is the change in position from time $i$ to $i + 1$.

Now say that the turtle's movement is determined by $k$ seed parameters drawn from
the same set. Then, for some state space $\mathcal{S}$,
define $s_i^j \in \mathcal{S}$ to be some arbitrary
state associated with timestamp $i$ for the $j$th seed parameter where $j \in [k]$.
Also, define $\pmb{s}_i = (s_i^1, s_i^2, ..., s_i^k)$.
Next we will define a set of functions $SU^j: \mathcal{S} \rightarrow \mathcal{S}$
(for $S$tate $U$pdater) such that $s_{i + 1}^j = SU^j(s_i^j, i)$. Note that for
$j, a \in [m]$ where $j \neq a$, $s_{i+1}^j$ is determined solely by $s_i^j$ and $i$ and not
$s_i^a$.

Now that we have our machinery built up, lets define $Comb: \mathcal{S}^k \rightarrow \R^d$ such that
$$
  \Delta p_{i + 1} = Comb\left(s^1_{i + 1}, s^2_{i + 1}, ..., s^k_{i + 1}\right).
$$
In other words, $Comb$ takes in the state of each seed and
returns an update to the position of the turtle.

Finally, let us define
$$
  \Delta P_{a, b} = \sum_{i = a}^{b} \Delta p_i.
$$
In other words, $\Delta P_{a, b}$ is the change in position from timestep $a$ to $b$.

\subsection{The problem}
Say we are given, $Comb$, hh$SU^j$, $p_0$, and $s^j_0$ for all $j \in [k]$.
Informally, the question is whether the turtle draws a ``closed" shape or not.\\
More formally, is there some period $T$ such that 
$$
  p_{i + \ell T} = p_{i}
$$
for $i, \ell \in \N$.
Then, note that if there exists a period $T$ such that 
$\Delta P_{i, i + \ell T} = 0$ for all $i, \ell \in N$, 
$p_{i + \ell T} = p_{i}$ and the turtle forms a closed shape.

% TODO: ask closure question
% TODO: show result that if $(s_{a}^1, ... ) = (s_{b}^1,...)$ then $b-a$ is a period for the state
% and Delta p_a = p_b and is thus invariant under mod b-a. So, if Delta p_{b-a} \neq 0 
% we have that the turtle will not move in a closed shape. If Delta p_{b-a} = 0, it will

\subsection{Specifying the task ahead of us}
For our case, we consider $Comb, SU^j$ to all be memoryless (i.e.\ there output
is uniquely determined by the current input). So, we can simplify the overall question.
If, $\pmb{s}_i = \pmb{s}_{i + \ell T}$ for some $T \in \N$ and all $i \in \N$, then 
$\Delta p_{i} = \Delta p_{i + \ell T}$. So then,
$\Delta P_{i, i + \ell T} = \Delta P_{i, i + \ell' T}$ for all $\ell, \ell' \in \N$.
Thus, $T$ is a period of the change in position. We can thus
break down our problem into two parts:
\begin{enumerate}
  \item Finding the period, $T$, of the state $\pmb{s}$.
  \item Checking whether $\Delta P_{i, i + T} = 0$.
\end{enumerate}

\subsection{Some more restrictions on our problem}
We further restrict the problem by only considering the case where
$$
  Comb((., ., ., ., \theta^1), (., ., ., ., \theta^2), ..., (., ., ., ., \theta^k)) =
    \left(\prod_{i=1}^k \cos(\theta_j) ^ {\mathrm{incl}_1^j}, ..., \prod_{i=1}^k \cos(\theta_j) ^ {\mathrm{incl}_D^j}\right)
$$
where $\mathrm{incl}_d^j \in \set{0, 1}$ for $d \in [D]$ indicates whether to include a given
$x \in R$ determined by seed $j$ for position update in the $d$th dimension.

We will also let $\mathcal{S} = N^5$ where for $(n, d, b, \theta) \in \mathcal{S}$,
$n$ is the numerator of a rational in fraction form, $d$ is the denominator, 
$b$ is the base (i.e\. base 10, base 12, etc.), $i$ is the current time step,
and $\frac{2\theta}{b \pi}$ is an ``angle" associated with the state.
Moreover, we will only consider
$$
  SU^j(n, b, d, \theta) = (n, b, d, \theta + \mathrm{digit}(n, b, d, i) \mod b).
$$

where $\mathrm{digit}(n, b, d, i)$ gives us the $i$th digit of the decimal expansion of $\frac{n}{d}$
in base $b$.

Finally, for simplicity's sake, assume that $\theta = 0$ for all $(n, b, d, \theta) \in \pmb{s}_0$,
$n < d$, and $\frac{n}{d}$'s decimal expansion is periodic after some $N \geq 0$ decimal places
and does not terminate in base $b$.

\subsubsection{Some intuition}
While the restrictions may seem arbitrary, they aptly match our original problem statement.
Take the three dimensional case with two seeds. The two seeds can be thought
of as the fraction which generates the updates to two angles, $\theta, \alpha$.
$\theta$ and $\alpha$ can then uniquely determine a direction in 3D space in which the 
turtle is pointing. 
So, at each time step $i + 1$, $\theta_{i + 1}$ equals to $\theta_i$, but rotated by
some fraction of $2 \pi$ determined by the $i$th digit of the decimal expansion of one fraction and its base.
% TODO: clear up.

% TODO: put your own diagram in!!

\section{Results}
\subsection{Finding period $T$}
\subsubsection{Finding the period of $\frac{n}{d}$}
We will first aim to find period $T$ of the state $\pmb{s}$.
For some $(n, b, d, \theta) \in \pmb{s}_0$, by \cite{MathOverflowFracPeriod},
we have that the period of the decimal expansion of $\frac{n}{d}$
can be determined by finding the smallest $\rationalPeriod$ such that
\begin{equation}
\label{eq:nd-period}
b ^ {\rationalPeriod} \equiv 1 \mod d.
\end{equation}
See, appendix \ref{AppendixPeriod} for more detail.
More generally though, any nontrivial $\rationalPeriod$ satisfying equation \ref{eq:nd-period}
will be a period of $\frac{n}{d}$.

\begin{remark}[Polytime]
  TODO: remark about polytime
\end{remark}

\subsubsection{Digital sum}
Next, we introduce the idea digitial sums.
For some number $N \in \N$, $N$ can be represented in base $b$ via
\begin{equation}
  N = \sum_{i=0}^{m} d_i b^i
\end{equation}
where $m = \lceil \log_b N \rceil$ and, $\forall i \in [m]$, $d_i \in \Z_b$.
Then, we define function $\mathrm{digSum}: \N \rightarrow \Z_b$
to give the digital sum such that
\begin{equation}
  \mathrm{digSum}(N) = \sum_{i=0}^{m} d_i.
\end{equation}

Moreover, define function $\mathrm{digSumPeriodic}: \N^4 \rightarrow \Z_b$
such that
% TODO: define T within the func from another func
\begin{equation}
  \mathrm{digSumPeriodic}(n, d, b) = \sum_{i = i_0}^{i_0 + T} \mathrm{digit}(n, d, b, i)
\end{equation}

\begin{remark}[Finding the digit sum of a rational]
  aaaa
\end{remark}

\subsubsection{Finding the period of $\seedAngleNotime$} % TODO: redifine things in terms of theta...
For $(n^j, b^j, d^j, \theta_i^j) = s_i^j$,
recall that $\seedAngle{i + 1} = \seedAngle{i} + \mathrm{digit}(n, b, d, i) \mod b$.
So, after period $\rationalPeriod$,
\begin{align*}
  \theta_{i + \rationalPeriod} &= \left(\theta_{i} + \sum_{\ell = i}^{\rationalPeriod + i} \mathrm{digit}(n, b, d, \ell)\right) \mod b\\
  &= \left(\theta_{i} + \mathrm{digSumPeriodic}(n, b, d)\right) \mod b\\
  &= \theta_{i} \mod b + \mathrm{digSumPeriodic}(n, b, d) \mod b.
\end{align*}
So, after $p$ periods of length $\rationalPeriod$ where $p \cdot \mathrm{digSumPeriodic}(n, b, d) \equiv 0 \mod b$,
$$
\theta_{i + p\rationalPeriod} = \theta_i.
$$
For simplicity, lets define
$$
  T^j = p\rationalPeriod
$$
where $T^j$ is the period of the state for seed $j$.
TODO: remove $i$ from the state and somehow have it be implicit....

\subsubsection{Finding the period of $\pmb{s}$}
We can first see that for $\stateNotime{j} \in \pmb{s}$, $\stateNotime{j}$
has period of $\statePeriod$. So, $\pmb{s}$ must have a period, $\totalPeriod$, of
$$
\lcm{j \in [k]}\; T^j.
$$
I.e.\ $\pmb{s}_i = \pmb{s}_{i + T}$ for all $i \in \N$.

% TODO: cite https://math.stackexchange.com/questions/377683/length-of-period-of-decimal-expansion-of-a-fraction
% TODO: formula in poly time
% TODO: hmmm... specify i > n_0 (to get rid of initial stuff...)

% https://en.wikipedia.org/wiki/Digital_root#:~:text=The%20digital%20root%20(also%20repeated,single%2Ddigit%20number%20is%20reached.

% \subsection{$\Delta P_{i, i + T} = 0$?}
% A bunch of sums and multiplies
% \cite{watrous2018theory}

\section{Conclusion}

\section{Open Questions}

\section*{Acknowledgments}

\appendix
\section{Finding the period of $\frac{n}{d}$}
\label{AppendixPeriod}
aaaaa

\bibliographystyle{alpha}
\bibliography{bib/ref}

\end{document}

### 2022-05-08 paper/Paper.tex
prog

@@
 \newcommand{\rationalPeriod}{{T^j}'}
+\newcommand{\rationalPeriodTotal}{{T}'}
 \newcommand{\statePeriod}{T^j}
-\newcommand{\seedAngle}[1]{{\theta_{#1}}^j}
+\newcommand{\seedAngle}[1]{{\theta^j_{#1}}}
 \newcommand{\seedAngleNotime}{{\theta}^j}
@@
 \newcommand{\totalPeriod}{T}
+\newcommand{\totalState}{\pmb{s}_i}
+\newcommand{\totalStateNotime}{\pmb{s}}
+\newcommand{\comb}{Comb}
+\newcommand{\combWithState}[1]{Comb\left(s^1_{#1}, s^2_{#1}, ..., s^k_{#1}\right)}
+\newcommand{\inclIndic}[2]{{\mathrm{incl}_{#1}^{#2}}}
+\newcommand{\combSingleTerm}[1]{\prod_{j=1}^k \cos(\theta_j) ^ {\inclIndic{#1}{j}}}
+\newcommand{\digSumPeriodic}{\mathrm{digSumPeriodic}^j}
 
@@
 $$
-  \Delta p_{i + 1} = Comb\left(s^1_{i + 1}, s^2_{i + 1}, ..., s^k_{i + 1}\right).
+  \Delta p_{i + 1} = \combWithState{i + 1}.
 $$
@@
   Comb((., ., ., ., \theta^1), (., ., ., ., \theta^2), ..., (., ., ., ., \theta^k)) =
-    \left(\prod_{i=1}^k \cos(\theta_j) ^ {\mathrm{incl}_1^j}, ..., \prod_{i=1}^k \cos(\theta_j) ^ {\mathrm{incl}_D^j}\right)
+    \left(\combSingleTerm{1}, ..., \combSingleTerm{D}\right)
 $$
@@
 
+Next, let $$
+\rationalPeriodTotal = \lcm{j \in [k]}\; \rationalPeriod.
+$$
+
 \begin{remark}[Polytime]
@@
 % TODO: define T within the func from another func
+% TODO: bettr defn
 \begin{equation}
-  \mathrm{digSumPeriodic}(n, d, b) = \sum_{i = i_0}^{i_0 + T} \mathrm{digit}(n, d, b, i)
+  \digSumPeriodic = \sum_{i = i_0}^{i_0 + \rationalPeriod} \mathrm{digit}(n, d, b, i)
 \end{equation}
@@
 
-\subsubsection{Finding the period of $\seedAngleNotime$} % TODO: redifine things in terms of theta...
+\subsubsection{Finding a period of $\seedAngleNotime$} % TODO: redifine things in terms of theta...
 For $(n^j, b^j, d^j, \theta_i^j) = s_i^j$,
 recall that $\seedAngle{i + 1} = \seedAngle{i} + \mathrm{digit}(n, b, d, i) \mod b$.
-So, after period $\rationalPeriod$,
+So, after period $\rationalPeriodTotal$,
 \begin{align*}
-  \theta_{i + \rationalPeriod} &= \left(\theta_{i} + \sum_{\ell = i}^{\rationalPeriod + i} \mathrm{digit}(n, b, d, \ell)\right) \mod b\\
-  &= \left(\theta_{i} + \mathrm{digSumPeriodic}(n, b, d)\right) \mod b\\
-  &= \theta_{i} \mod b + \mathrm{digSumPeriodic}(n, b, d) \mod b.
+  \theta_{i + \rationalPeriodTotal} &= \left(\theta_{i} + \sum_{\ell = i}^{\rationalPeriodTotal + i} \mathrm{digit}(n, b, d, \ell)\right) \mod b\\
+  &= \left(\theta_{i} + \frac{\rationalPeriodTotal}{\rationalPeriod} \digSumPeriodic\right) \mod b\\
+  &= \theta_{i} \mod b + \frac{\rationalPeriodTotal}{\rationalPeriod} \digSumPeriodic \mod b.
 \end{align*}
-So, after $p$ periods of length $\rationalPeriod$ where $p \cdot \mathrm{digSumPeriodic}(n, b, d) \equiv 0 \mod b$,
+So, after $p$ periods of length $\rationalPeriodTotal$ where $p \cdot \frac{\rationalPeriodTotal}{\rationalPeriod}  \cdot \digSumPeriodic \equiv 0 \mod b$,
 $$
-\theta_{i + p\rationalPeriod} = \theta_i.
+\theta_{i + p\rationalPeriodTotal} = \theta_i.
 $$
@@
 $$
-  T^j = p\rationalPeriod
+  T^j = p\rationalPeriodTotal
 $$
-where $T^j$ is the period of the state for seed $j$.
-TODO: remove $i$ from the state and somehow have it be implicit....
+where $T^j$ is a period of the state for seed $j$.
+% TODO: remove $i$ from the state and somehow have it be implicit....
 
+% Oh man... we are going to have to define an intermediate total period...
+% One for all T'...
+% and then have a sum for T
 \subsubsection{Finding the period of $\pmb{s}$}
@@
 
-% \subsection{$\Delta P_{i, i + T} = 0$?}
+\subsection{Does it close? $\Delta P_{i, i + T} = 0$?}
+So now that we know the period of $\totalStateNotime$, we can ask if
+$\Delta P_{i, i + T} = 0$. % TODO: reference
+
+Note that 
+$$
+\Delta P_{i, i + T} = \Delta P_{q, q + T}
+$$
+for all $i, q \in \N$ by definition of periodicity.
+So, we will drop the $i$ and replace it with a $0$.
+Then,
+\begin{align*}
+  \Delta P_{0, T} &= \sum_{i = 1}^T \Delta p_i \\
+  &= \sum_{i = 1}^T \combWithState{i} \\
+  &= \sum_{i = 1}^T \left(\combSingleTerm{1}, ..., \combSingleTerm{D}\right) \\
+  &= \left(\sum_{i = 1}^T \combSingleTerm{1}, ..., \sum_{i = 1}^T \combSingleTerm{D}\right).
+\end{align*}
+We can thus see that $\Delta P_{0, T} = \pmb{0} = (0, ..., 0)$ iff 
+\begin{equation}
+\label{eq:singleDelta0}
+\sum_{i = 1}^T \combSingleTerm{d} = 0
+\end{equation}
+for all $d \in D$.
+
+\subsubsection{Closing along a single dimension}
+Finally, to see if a shape will close,
+we just need to find if equation \eqref{eq:singleDelta0} holds true for all dimensions.
+First, let $A_d = \set{j \mid j \in [k] \and \inclIndic{d}{j} = 1}$
+We can then see that
+\begin{align*}
+&\sum_{i = 1}^T \combSingleTerm{d}\\
+&=\sum_{i = 1}^T \prod_{j = 1}^k \left(\half \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\right)^\inclIndic{d}{j}\\
+&=2^{-|A|} \sum_{i = 1}^T \prod_{j \in A_d} \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\\
+\end{align*}
+
+\newcommand{\periodFrac}{\frac{\totalPeriod}{\rationalPeriod}}
+\newcommand{\periodFracRational}{\frac{\rationalPeriodTotal}{\rationalPeriod}}
+
+We can then see that for $(n, b, d, \theta_i) \in \pmb{s}_i$
+\begin{align*}
+  \seedAngle{x \rationalPeriodTotal + y} &= \sum_{i = 0}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, i) \\
+  &= \sum_{p = 0}^{x\periodFrac - 1} \sum_{q=0}^{\rationalPeriod - 1} \mathrm{digit}(n, b, d, p\rationalPeriodTotal + b)
+    + \sum_{p = 0}  \\
+    % ARGS::....
+  &= x\cdot \periodFracRational \cdot \digSumPeriodic + .
+\end{align*}
+
+Then, 
+\begin{align*}
+ &2^{-|A|} \sum_{i = 1}^T \prod_{j \in A_d} \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\\
+ =& 2^{-|A|} \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}\prod_{j \in A_d} \left(e^{\seedAngle{p \rationalPeriodTotal + q} I} +  e^{-\seedAngle{p \rationalPeriodTotal + q} I}\right)\\
+\end{align*}
+
 % A bunch of sums and multiplies
@@
 \end{document}
+
+% TODO: put b\theta / 2pi in State UPDATE

### 2022-05-08 paper/Paper.tex
prog

@@
 \newcommand{\statePeriod}{T^j}
+\newcommand{\seedAngleJ}[2]{{\theta^{#2}_{#1}}}
 \newcommand{\seedAngle}[1]{{\theta^j_{#1}}}
@@
 \subsubsection{Digital sum}
-Next, we introduce the idea digitial sums.
+Next, we introduce the idea digital sums.
 For some number $N \in \N$, $N$ can be represented in base $b$ via
@@
 
-Moreover, define function $\mathrm{digSumPeriodic}: \N^4 \rightarrow \Z_b$
+Moreover, define function $\digSumPeriodic \in \Z_b$
 such that
@@
 \begin{equation}
-  \digSumPeriodic = \sum_{i = i_0}^{i_0 + \rationalPeriod} \mathrm{digit}(n, d, b, i)
+  \digSumPeriodic = \sum_{i = i_0}^{i_0 + \rationalPeriodTotal} \mathrm{digit}(n, d, b, i)
 \end{equation}
@@
   \theta_{i + \rationalPeriodTotal} &= \left(\theta_{i} + \sum_{\ell = i}^{\rationalPeriodTotal + i} \mathrm{digit}(n, b, d, \ell)\right) \mod b\\
-  &= \left(\theta_{i} + \frac{\rationalPeriodTotal}{\rationalPeriod} \digSumPeriodic\right) \mod b\\
-  &= \theta_{i} \mod b + \frac{\rationalPeriodTotal}{\rationalPeriod} \digSumPeriodic \mod b.
+  &= \left(\theta_{i} +  \digSumPeriodic\right) \mod b\\
+  &= \theta_{i} \mod b +  \digSumPeriodic \mod b.
 \end{align*}
-So, after $p$ periods of length $\rationalPeriodTotal$ where $p \cdot \frac{\rationalPeriodTotal}{\rationalPeriod}  \cdot \digSumPeriodic \equiv 0 \mod b$,
+So, after $p$ periods of length $\rationalPeriodTotal$ where $p  \cdot \digSumPeriodic \equiv 0 \mod b$,
 $$
@@
 we just need to find if equation \eqref{eq:singleDelta0} holds true for all dimensions.
-First, let $A_d = \set{j \mid j \in [k] \and \inclIndic{d}{j} = 1}$
+First, let $A_d = \set{j \mid j \in [k] \; ; \inclIndic{d}{j} = 1}$
 We can then see that
@@
 
-We can then see that for $(n, b, d, \theta_i) \in \pmb{s}_i$
+We can then see that for $(n, b, d, \theta_i) \in \pmb{s}_i$ and $x, y \in \N$ where $y < \rationalPeriodTotal$,
+\begin{align}
+  \seedAngle{x \rationalPeriodTotal + y} &= \sum_{i = 0}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, i) \notag \\
+  &= \sum_{p = 0}^{(x- 1)\rationalPeriodTotal} \sum_{q=0}^{\rationalPeriodTotal - 1} \mathrm{digit}(n, b, d, p\rationalPeriodTotal + q)
+    + \sum_{p = x \rationalPeriodTotal}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, p) \notag \\
+    % ARGS::....
+  \label{eq:angleBreakdown}
+  &= x \cdot \digSumPeriodic + \sum_{p = x \rationalPeriodTotal}^{\rationalPeriodTotal + y}\mathrm{digit}(n, b, d, p) \notag \\
+  &= x \cdot \digSumPeriodic + \sum_{p = 0}^{y}\mathrm{digit}(n, b, d, p)
+\end{align}
+because $\mathrm{digit}(n, b, d, x\rationalPeriodTotal + \ell) = \mathrm{digit}(n, b, d, \ell)$ for any $\ell \in \N$
+by definition of periodicity.
+
+Observe that 
 \begin{align*}
-  \seedAngle{x \rationalPeriodTotal + y} &= \sum_{i = 0}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, i) \\
-  &= \sum_{p = 0}^{x\periodFrac - 1} \sum_{q=0}^{\rationalPeriod - 1} \mathrm{digit}(n, b, d, p\rationalPeriodTotal + b)
-    + \sum_{p = 0}  \\
-    % ARGS::....
-  &= x\cdot \periodFracRational \cdot \digSumPeriodic + .
+ &\prod_{j \in A_d} \left(e^{\seedAngle{p \rationalPeriodTotal + q} I} +  e^{-\seedAngle{p \rationalPeriodTotal + q} I}\right) \\
+ =& \exp(\seedAngleJ{p \rationalPeriodTotal + q}{1} + \seedAngleJ{p \rationalPeriodTotal + q}{2} + ... + \seedAngleJ{p \rationalPeriodTotal + q}{d}) 
+  + \exp(\seedAngleJ{p \rationalPeriodTotal + q}{1} - \seedAngleJ{p \rationalPeriodTotal + q}{2} + ... + \seedAngleJ{p \rationalPeriodTotal + q}{d}) + ... \\
+  &+ \exp(\seedAngleJ{p \rationalPeriodTotal + q}{1} - \seedAngleJ{p \rationalPeriodTotal + q}{2} - ... - \seedAngleJ{p \rationalPeriodTotal + q}{d})
 \end{align*}
+which then equals
+\begin{equation}
+ \sum_{\beta \in \set{0,1}^{|A_d|}} 
+    \exp\left(
+        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
+        \seedAngle{p \rationalPeriodTotal + q}I
+      \right).
+\end{equation}
 
@@
  =& 2^{-|A|} \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}\prod_{j \in A_d} \left(e^{\seedAngle{p \rationalPeriodTotal + q} I} +  e^{-\seedAngle{p \rationalPeriodTotal + q} I}\right)\\
+ =&
+  2^{-|A|} \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
+ \sum_{\beta \in \set{0,1}^{|A_d|}} 
+    \exp\left(
+        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
+        \seedAngle{p \rationalPeriodTotal + q}I
+      \right)\\
+ =&
+  2^{-|A|} 
+ \sum_{\beta \in \set{0,1}^{|A_d|}} 
+     \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
+    \exp\left(
+        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
+        \seedAngle{p \rationalPeriodTotal + q}I
+      \right).
 \end{align*}
+
+Then, lets fix some $\beta \in \set{0, 1}^{|A_d|}$, we will now show that 
+\begin{equation}
+\label{eq:wts01}  
+  \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
+    \exp\left(
+        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
+        \seedAngle{p \rationalPeriodTotal + q}I
+      \right)
+\end{equation}
+always equals $0$ or $1$ for any choice of $\beta$.
+
+Observe that 
+\begin{align}
+  \exp(\seedAngle{p \rationalPeriodTotal + q}I) &= \exp\left(p \cdot \digSumPeriodic +
+    \sum_{\ell = p \rationalPeriodTotal}^{p \rationalPeriodTotal + q}\mathrm{digit}(n, b, d, \ell)\right) \tag{by equation \eqref{eq:angleBreakdown}} \\
+    \label{eq:expBreakdown}
+    &= \exp\left(p \cdot \digSumPeriodic\right) \exp\left(\sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)\right).
+\end{align}
+
+So then, by equation \eqref{eq:expBreakdown}, we get that
+\begin{align}
+&\exp\left(
+    \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
+    \seedAngle{p \rationalPeriodTotal + q}I = 
+\right)\notag \\ 
+\label{eq:decomposeExp}
+=&
+\exp\left(
+    \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
+    \cdot p \cdot
+    \digSumPeriodic
+\right)
+\exp\left(
+    \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
+      \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell).
+\right).
+\end{align}
+
+We then use \eqref{eq:decomposeExp} to show that \eqref{eq:wts01} equals
+\begin{equation*}
+  \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \left[
+    \exp\left(
+      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
+      \digSumPeriodic
+    \right)
+  \left(
+  \sum_{q = 0}^{\rationalPeriodTotal - 1}
+    \exp\left(
+        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
+          \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell).
+    \right)\right)\right].
+\end{equation*}
+% TODO: second part can be thought of as a constant for now... ie C2=
+% Then, we can think of the inner first sum as a constant of sorts, (C1)
+% And we know that pI(T/T') = 1 and that pI0 = 1. So, if C1 \neq 0, we get some roots of unity
+% and then the whole sum is 0...
+% If it does equal 0, you have to check if C2 = 0... don't really know how to do this...
+% If C1 = 0 and C2 not equal to 0, then
+
+% TODO: then think of notation for the "distributed" polynomial, then you can expand...
+% / assignment of +- strings... oy vey
+
+% TODO: no clue what is going on with C2... (maybe throw in some pictures...)
+
+% TODO: overall goal, show this is in coNP...
 

### 2022-05-09 paper/Paper.tex
main result 1

@@
 \newcommand{\digSumPeriodic}{\mathrm{digSumPeriodic}^j}
+\newcommand{\digSumPeriodicNoJ}{\mathrm{digSumPeriodic}}
+\newcommand{\totalOverRationalFrac}{\frac{\totalPeriod}{\rationalPeriodTotal}}
 
@@
 \begin{remark}[Polytime]
-  TODO: remark about polytime
+  TODO: remark about discrete log and similarity... (we think this is hard, but in QPP)...
 \end{remark}
@@
 
-Then, lets fix some $\beta \in \set{0, 1}^{|A_d|}$, we will now show that 
-\begin{equation}
-\label{eq:wts01}  
+\newcommand{\eqWTSInnerProd}{
   \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
@@
         \seedAngle{p \rationalPeriodTotal + q}I
-      \right)
+      \right)}
+
+Then, lets fix some $\beta \in \set{0, 1}^{|A_d|}$, we will now show that 
+\begin{equation}
+\label{eq:wts01}  
+  \eqWTSInnerProd
 \end{equation}
@@
 We then use \eqref{eq:decomposeExp} to show that \eqref{eq:wts01} equals
-\begin{equation*}
+\begin{equation}
+\label{eq:inner-outer-split}
   \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \left[
@@
         \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-          \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell).
+          \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)
     \right)\right)\right].
+\end{equation}
+
+\subsubsection*{Case 1}
+Observe that the inner sum,
+$
+  \sum_{q = 0}^{\rationalPeriodTotal - 1}
+  \exp\left(
+      \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
+        \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)
+  \right)
+$,
+is invariant for all $p$ in equitation \eqref{eq:inner-outer-split}. So then,
+let the inner sum equal $C \in \Z$.  Moreover, note that 
+\begin{align*}
+  &\exp\left(
+      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
+      \digSumPeriodic
+    \right)\\
+  =& \prod_{j \in A_d} \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right)
+\end{align*}
+and that 
+\begin{equation*}
+  \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right) = \exp\left(0\right) = 1
 \end{equation*}
+when $p = \frac{\totalPeriod}{\rationalPeriodTotal}$. Then, we can see that
+$$
+\prod_{j \in A_d} \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right) = 1
+$$
+when $p = \frac{\totalPeriod}{\rationalPeriodTotal}$.
+
+And so, because $\digSumPeriodic$ is a constant, we can conclude that
+\begin{equation*}
+ \exp\left(
+      I \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
+      \digSumPeriodic
+    \right) 
+\end{equation*}
+is a $\totalOverRationalFrac^th$ root of unity iff $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \neq 0$.
+
+So, for $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \neq 0$, we have that
+\begin{align*}
+  \eqWTSInnerProd &= C \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1}
+    \exp\left(
+      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
+      \digSumPeriodic
+    \right) \\
+    &= C \sum_{p = 0}^{\totalOverRationalFrac - 1}\exp\left(W_{\totalOverRationalFrac}^p\right) \\
+    &= 0.
+\end{align*}
+where $W_{\totalOverRationalFrac}^p$ is the $\totalOverRationalFrac^{th}$ root of unity.
+
+If $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} = 0$, then 
+\begin{align*}
+  \eqWTSInnerProd &= C \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \exp(0) \\
+  &= 1.
+\end{align*}
+
+So, we have now shown that \eqref{eq:wts01} is always $0$ or $1$. In particular, we also have our first 
+closure result. If, $\forall \beta \in \set{0, 1}^{|A_d|}$, $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \neq 0$,
+\begin{align*}
+  \sum_{i = 1}^T \combSingleTerm{d} &=  2^{-|A|} 
+  \sum_{\beta \in \set{0,1}^{|A_d|}} 
+      \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
+     \exp\left(
+         \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
+         \seedAngle{p \rationalPeriodTotal + q}I
+       \right) \\
+        &= 0
+\end{align*}
+for all $d \in D$.
+So then, $\Delta P_{0, T} = 0$ whenever 
+no degree $1$ multinomials with coefficients of $-1$ or $1$ and $|A_d|$ variables has a root of $(\digSumPeriodicNoJ^1, \digSumPeriodicNoJ^2, ..., \digSumPeriodicNoJ^{|A_d|})$.
+In other words, if variables, $x_1 = \digSumPeriodicNoJ^1, x_2 = \digSumPeriodicNoJ^2, ...$, there does not exist a multinomial
+of form $\pm x_1 \pm x_2 \pm ... \pm x_{|A_d|} = 0$.
+
 % TODO: second part can be thought of as a constant for now... ie C2=

### 2022-05-09 paper/Paper.tex
prog

@@
 is invariant for all $p$ in equitation \eqref{eq:inner-outer-split}. So then,
-let the inner sum equal $C \in \Z$.  Moreover, note that 
+let the inner sum equal $C_\beta \in \Z$.  Moreover, note that 
 \begin{align*}
@@
 In other words, if variables, $x_1 = \digSumPeriodicNoJ^1, x_2 = \digSumPeriodicNoJ^2, ...$, there does not exist a multinomial
-of form $\pm x_1 \pm x_2 \pm ... \pm x_{|A_d|} = 0$.
+of form 
+$$
+  \pm x_1 \pm x_2 \pm ... \pm x_{|A_d|} = 0.
+$$
+
+% TODO: replace this eqWTSInnerProf with like P_{}(d) or smthng...
+In the case that $\exists \beta \in \set{0, 1}^{|A_d|}$ such that $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} = 0$, it is still possible
+for
+$$
+\eqWTSInnerProd = 0
+$$
+if $C_\beta = 0$. So, 
+\begin{equation*}
+  \sum_{q = 0}^{\rationalPeriodTotal - 1}
+  \exp\left(
+      \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
+        \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)
+  \right) = 0
+\end{equation*}
 

### 2022-05-10 paper/Paper.tex
paper prog

@@
 \newcommand{\inclIndic}[2]{{\mathrm{incl}_{#1}^{#2}}}
-\newcommand{\combSingleTerm}[1]{\prod_{j=1}^k \cos(\theta_j) ^ {\inclIndic{#1}{j}}}
-\newcommand{\digSumPeriodic}{\mathrm{digSumPeriodic}^j}
-\newcommand{\digSumPeriodicNoJ}{\mathrm{digSumPeriodic}}
+\newcommand{\numbToAngle}{\frac{2\pi}{b^j}}
+\newcommand{\numbToAngleNoJ}[1]{\frac{2\pi}{b^{#1}}}
+\newcommand{\combSingleTerm}[1]{\prod_{j=1}^k \cos\left(\numbToAngle \cdot \theta^j\right) ^ {\inclIndic{#1}{j}}}
+\newcommand{\digSumPeriodic}{\sigma^j}
+\newcommand{\digSumPeriodicNoJ}{{\sigma}}
 \newcommand{\totalOverRationalFrac}{\frac{\totalPeriod}{\rationalPeriodTotal}}
+\newcommand{\changeTotalOneDim}{\Delta P_{0, T}^d}
+\newcommand{\digit}{\mathrm{digit}}
+\newcommand{\commonBase}{\pmb{b}}
+\newcommand{\numbToCommon}{\frac{\commonBase}{b^j}}
+\newcommand{\commonToAngle}{\frac{2\pi}{\commonBase}}
 
@@
 \subsection{Specifying the task ahead of us}
-For our case, we consider $Comb, SU^j$ to all be memoryless (i.e.\ there output
+For our case, we consider $Comb, SU_i^j$ to all be memoryless (i.e.\ there output
 is uniquely determined by the current input). So, we can simplify the overall question.
@@
 \subsection{Some more restrictions on our problem}
-We further restrict the problem by only considering the case where
+We further restrict the problem by only considering $\mathcal{S} = N^5$ where for $(n, d, b, \theta) \in \mathcal{S}$,
+$n$ is the numerator of a rational in fraction form, $d$ is the denominator, 
+$b$ is the base (i.e.\ base 10, base 12, etc.),
+and $\frac{2\theta}{b \pi}$ is an ``angle" associated with the state.
+Moreover, we will only consider
+$$
+  SU_i^j(n, b, d, \theta) = (n, b, d, \theta + \mathrm{digit}(n, b, d, i) \mod b).
+$$
+
+where $\mathrm{digit}(n, b, d, i)$ gives us the $i$th digit of the decimal expansion of $\frac{n}{d}$
+in base $b$.
+
+Moreover, we consider the case where
 $$
@@
 
-We will also let $\mathcal{S} = N^5$ where for $(n, d, b, \theta) \in \mathcal{S}$,
-$n$ is the numerator of a rational in fraction form, $d$ is the denominator, 
-$b$ is the base (i.e\. base 10, base 12, etc.), $i$ is the current time step,
-and $\frac{2\theta}{b \pi}$ is an ``angle" associated with the state.
-Moreover, we will only consider
-$$
-  SU^j(n, b, d, \theta) = (n, b, d, \theta + \mathrm{digit}(n, b, d, i) \mod b).
-$$
-
-where $\mathrm{digit}(n, b, d, i)$ gives us the $i$th digit of the decimal expansion of $\frac{n}{d}$
-in base $b$.
-
 Finally, for simplicity's sake, assume that $\theta = 0$ for all $(n, b, d, \theta) \in \pmb{s}_0$,
@@
 and does not terminate in base $b$.
+
+Also, lets set 
+$$\commonBase = \lcm{(n, b, d, \theta) \in \pmb{s}_0} b.$$
+In other words,
+$\commonBase$ can be thought of as a ``common base" among all seeds.
 
@@
 
-Moreover, define function $\digSumPeriodic \in \Z_b$
+Moreover, define $\digSumPeriodic \in \Z_b$
 such that
@@
 \begin{equation}
-  \digSumPeriodic = \sum_{i = i_0}^{i_0 + \rationalPeriodTotal} \mathrm{digit}(n, d, b, i)
+  \digSumPeriodic = \sum_{i = i_0}^{i_0 + \rationalPeriodTotal} \mathrm{digit}(n, d, b, i).
 \end{equation}
+In other words, $\rationalPeriodTotal$ is the digital sum over one period.
 
@@
 
+Before getting to the main result, we need to first prove the following lemma
+\begin{lemma}{For all $j \in [k]$ and $x, y \in \N$ where $y < \rationalPeriodTotal$, we have that 
+  $$
+    \theta_{xT' + y}^j = x\cdot \digSumPeriodic + \sum_{q = 0}^y \digit(n, b, d, q)
+  $$}
+  \label{lemma:angleBreakdown}
+  \begin{proof}
+    We can then see that for $(n, b, d, \theta_{x\rationalPeriodTotal + y}^j) \in \pmb{s}_{x\rationalPeriodTotal + y}$,
+    \begin{align*}
+      \seedAngle{x \rationalPeriodTotal + y} &= \sum_{i = 0}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, i) \\
+      &= \sum_{p = 0}^{(x- 1)\rationalPeriodTotal} \sum_{q=0}^{\rationalPeriodTotal - 1} \mathrm{digit}(n, b, d, p\rationalPeriodTotal + q)
+          + \sum_{q = x \rationalPeriodTotal}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, q)\\
+      &= x \cdot \digSumPeriodic + \sum_{q = x \rationalPeriodTotal}^{\rationalPeriodTotal + y}\mathrm{digit}(n, b, d, q)\\
+      &= x \cdot \digSumPeriodic + \sum_{q = 0}^{y}\mathrm{digit}(n, b, d, q)
+    \end{align*}
+    because $\mathrm{digit}(n, b, d, x\rationalPeriodTotal + \ell) = \mathrm{digit}(n, b, d, \ell)$ for any $\ell \in \N$
+    by definition of periodicity.
+  \end{proof}
+\end{lemma}
+
 \subsubsection{Closing along a single dimension}
-Finally, to see if a shape will close,
-we just need to find if equation \eqref{eq:singleDelta0} holds true for all dimensions.
-First, let $A_d = \set{j \mid j \in [k] \; ; \inclIndic{d}{j} = 1}$
+Let $\changeTotalOneDim$ be the change of position along dimension $d$
+from timestep 0 to $T$.
+We are now ready to determine if we ``close" along one dimension. I.e.\ does
+$
+\changeTotalOneDim = 0
+$?
+
+Define $A_d = \set{j \mid j \in [k] \; \text{and}\; \inclIndic{d}{j} = 1}$, in other words,
+$A_d$ is the set of seeds which are included in determining the position along the $d$th dimension.
 We can then see that
 \begin{align*}
-&\sum_{i = 1}^T \combSingleTerm{d}\\
-&=\sum_{i = 1}^T \prod_{j = 1}^k \left(\half \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\right)^\inclIndic{d}{j}\\
-&=2^{-|A|} \sum_{i = 1}^T \prod_{j \in A_d} \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\\
+\changeTotalOneDim &=\sum_{i = 1}^T \combSingleTerm{d}\\
+  &=\sum_{i = 1}^T \prod_{j = 1}^k \left(\half \left(\exp\left({\numbToAngle \seedAngle{i} I}\right) +  \exp\left(-\numbToAngle \seedAngle{i} I\right)\right)\right)^\inclIndic{d}{j}\\
+  &= 2^{-|A|} \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
+    \prod_{j \in A_d} \left(
+      \exp\left(\numbToAngle\seedAngle{p \rationalPeriodTotal + q} I\right) +  \exp\left(-\numbToAngle\seedAngle{p \rationalPeriodTotal + q} I\right)\right)
 \end{align*}
+by the Euler form of $\cos$.
 
@@
 
-We can then see that for $(n, b, d, \theta_i) \in \pmb{s}_i$ and $x, y \in \N$ where $y < \rationalPeriodTotal$,
-\begin{align}
-  \seedAngle{x \rationalPeriodTotal + y} &= \sum_{i = 0}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, i) \notag \\
-  &= \sum_{p = 0}^{(x- 1)\rationalPeriodTotal} \sum_{q=0}^{\rationalPeriodTotal - 1} \mathrm{digit}(n, b, d, p\rationalPeriodTotal + q)
-    + \sum_{p = x \rationalPeriodTotal}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, p) \notag \\
-    % ARGS::....
-  \label{eq:angleBreakdown}
-  &= x \cdot \digSumPeriodic + \sum_{p = x \rationalPeriodTotal}^{\rationalPeriodTotal + y}\mathrm{digit}(n, b, d, p) \notag \\
-  &= x \cdot \digSumPeriodic + \sum_{p = 0}^{y}\mathrm{digit}(n, b, d, p)
-\end{align}
-because $\mathrm{digit}(n, b, d, x\rationalPeriodTotal + \ell) = \mathrm{digit}(n, b, d, \ell)$ for any $\ell \in \N$
-by definition of periodicity.
-
-Observe that 
+% TODO: not entirely correct with d
+Next, observe that 
 \begin{align*}
- &\prod_{j \in A_d} \left(e^{\seedAngle{p \rationalPeriodTotal + q} I} +  e^{-\seedAngle{p \rationalPeriodTotal + q} I}\right) \\
- =& \exp(\seedAngleJ{p \rationalPeriodTotal + q}{1} + \seedAngleJ{p \rationalPeriodTotal + q}{2} + ... + \seedAngleJ{p \rationalPeriodTotal + q}{d}) 
-  + \exp(\seedAngleJ{p \rationalPeriodTotal + q}{1} - \seedAngleJ{p \rationalPeriodTotal + q}{2} + ... + \seedAngleJ{p \rationalPeriodTotal + q}{d}) + ... \\
-  &+ \exp(\seedAngleJ{p \rationalPeriodTotal + q}{1} - \seedAngleJ{p \rationalPeriodTotal + q}{2} - ... - \seedAngleJ{p \rationalPeriodTotal + q}{d})
+  &\prod_{j \in A_d} \left(
+      \exp\left(\numbToAngle\seedAngle{p \rationalPeriodTotal + q} I\right) +  \exp\left(-\numbToAngle\seedAngle{p \rationalPeriodTotal + q} I\right)\right)\\
+ =& 
+  \exp(\numbToAngleNoJ{1}\seedAngleJ{p \rationalPeriodTotal + q}{1} + \numbToAngleNoJ{2}\seedAngleJ{p \rationalPeriodTotal + q}{2} + ...
++ \numbToAngleNoJ{d}\seedAngleJ{p \rationalPeriodTotal + q}{d})
+  + \exp(\numbToAngleNoJ{1}\seedAngleJ{p \rationalPeriodTotal + q}{1} - \numbToAngleNoJ{2}\seedAngleJ{p \rationalPeriodTotal + q}{2} + ...
++ \numbToAngleNoJ{d}\seedAngleJ{p \rationalPeriodTotal + q}{d}) + ...
+\\
+  &+ \exp(-\numbToAngleNoJ{1}\seedAngleJ{p \rationalPeriodTotal + q}{1} - \numbToAngleNoJ{2}\seedAngleJ{p \rationalPeriodTotal + q}{2} - ...
+- \numbToAngleNoJ{d}\seedAngleJ{p \rationalPeriodTotal + q}{d})
 \end{align*}
@@
     \exp\left(
+      	\commonToAngle I
         \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-        \seedAngle{p \rationalPeriodTotal + q}I
-      \right).
+          \numbToCommon \seedAngle{p \rationalPeriodTotal + q}
+      \right)
 \end{equation}
+where $\beta$ can be though of as a bit string deciding whether the angle from seed
+$j \in A_d$ is added to or subtracted from the exponent.
 
-Then, 
+Then, we have that
+% TODO: update with common base stuff...
 \begin{align*}
- &2^{-|A|} \sum_{i = 1}^T \prod_{j \in A_d} \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\\
- =& 2^{-|A|} \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}\prod_{j \in A_d} \left(e^{\seedAngle{p \rationalPeriodTotal + q} I} +  e^{-\seedAngle{p \rationalPeriodTotal + q} I}\right)\\
- =&
+ \changeTotalOneDim =&
   2^{-|A|} \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
@@
 
-Then, lets fix some $\beta \in \set{0, 1}^{|A_d|}$, we will now show that 
+Then, lets fix some $\beta \in \set{0, 1}^{|A_d|}$, define $Q$ such that
 \begin{equation}
 \label{eq:wts01}  
-  \eqWTSInnerProd
+  Q = \eqWTSInnerProd.
 \end{equation}
-always equals $0$ or $1$ for any choice of $\beta$.
+We will simplify $Q$ to show 2 distinct cases where $Q = 0$ for any choice of $\beta$.
 
@@
 \begin{align}
-  \exp(\seedAngle{p \rationalPeriodTotal + q}I) &= \exp\left(p \cdot \digSumPeriodic +
-    \sum_{\ell = p \rationalPeriodTotal}^{p \rationalPeriodTotal + q}\mathrm{digit}(n, b, d, \ell)\right) \tag{by equation \eqref{eq:angleBreakdown}} \\
+  \exp(\seedAngle{p \rationalPeriodTotal + q}I)
+  &= \exp\left(p \cdot \digSumPeriodic +
+    \numbToCommon \sum_{\ell = p \rationalPeriodTotal}^{p \rationalPeriodTotal + q}\mathrm{digit}(n^j, b^j, d^j, \ell)\right) \tag{by lemma \ref{lemma:angleBreakdown}} \\
     \label{eq:expBreakdown}
-    &= \exp\left(p \cdot \digSumPeriodic\right) \exp\left(\sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)\right).
+    &= \exp\left(p \cdot \digSumPeriodic\right) \exp\left(\numbToCommon \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)\right).
 \end{align}
@@
     \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-    \seedAngle{p \rationalPeriodTotal + q}I = 
+    \seedAngle{p \rationalPeriodTotal + q}I
 \right)\notag \\ 
@@
 \exp\left(
-    \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-      \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell).
+    \sum_{j \in A_d} -1 ^ {\beta_{(j)}} \numbToCommon
+      \sum_{\ell = 0}^{q}\mathrm{digit}(n^j, b^j, d^j, \ell).
 \right).
@@
 
-We then use \eqref{eq:decomposeExp} to show that \eqref{eq:wts01} equals
+We then use \eqref{eq:decomposeExp} to show that $Q$ equals
 \begin{equation}
@@
     \exp\left(
-        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-          \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)
+        \sum_{j \in A_d} -1 ^ {\beta_{(j)}} \numbToCommon
+          \sum_{\ell = 0}^{q}\mathrm{digit}(n^j, b^j, d^j, \ell)
     \right)\right)\right].
@@
 \subsubsection*{Case 1}
-Observe that the inner sum,
-$
-  \sum_{q = 0}^{\rationalPeriodTotal - 1}
+Define
+$$
+  C_\beta = \sum_{q = 0}^{\rationalPeriodTotal - 1}
   \exp\left(
-      \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
+      \sum_{j \in A_d} -1 ^ {\beta_{(j)}} \numbToCommon
         \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)
-  \right)
-$,
-is invariant for all $p$ in equitation \eqref{eq:inner-outer-split}. So then,
-let the inner sum equal $C_\beta \in \Z$.  Moreover, note that 
+  \right).
+$$
+Moreover, note that 
 \begin{align*}
@@
       \digSumPeriodic
-    \right)\\
-  =& \prod_{j \in A_d} \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right)
+    \right)
+  = \prod_{j \in A_d} \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right)
 \end{align*}
@@
 \end{equation*}
-when $p = \frac{\totalPeriod}{\rationalPeriodTotal}$. Then, we can see that
+when $p = \frac{\totalPeriod}{\rationalPeriodTotal}$. So, we can see that
 $$
@@
 
-And so, because $\digSumPeriodic$ is a constant, we can conclude that
+Because $\digSumPeriodic$ is a constant, we can conclude that
 \begin{equation*}
@@
 \end{equation*}
-is a $\totalOverRationalFrac^th$ root of unity iff $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \neq 0$.
+is a $\totalOverRationalFrac^{th}$ root of unity iff 
+$$\sum_{j \in A_d} -1 ^ {\beta_{(j)}}\digSumPeriodic \neq 0$$
 
-So, for $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \neq 0$, we have that
+So, for $\sum_{j \in A_d} -1 ^ {\beta_{(j)}}\digSumPeriodic \neq 0$, we have that
 \begin{align*}
-  \eqWTSInnerProd &= C \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1}
+  \eqWTSInnerProd &= C_\beta \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1}
     \exp\left(
@@
     \right) \\
-    &= C \sum_{p = 0}^{\totalOverRationalFrac - 1}\exp\left(W_{\totalOverRationalFrac}^p\right) \\
+    &= C_\beta \sum_{p = 0}^{\totalOverRationalFrac - 1}\exp\left(W_{\totalOverRationalFrac}^p\right) \\
     &= 0.
@@
 
-If $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} = 0$, then 
+If $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \digSumPeriodic = 0$, then 
 \begin{align*}
-  \eqWTSInnerProd &= C \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \exp(0) \\
-  &= 1.
+  \eqWTSInnerProd &= C_\beta \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \exp(0) \\
+  &= C_\beta.
 \end{align*}
@@
 $$
+
+Said differently, let multinomial $m: \Z_{\commonBase} \rightarrow \Z_{\commonBase}$ be such that
+\begin{equation*}
+  m(x_1, x_2, ..., x_{|A_d|}) = \prod_{\beta \in \set{0, 1}^{|A_d|}} \left(\sum_{j \in A_d} -1^{\beta_j}AAA \right).
+\end{equation*}
+Then, if $m(\digSumPeriodicNoJ^1, \digSumPeriodicNoJ^2, ..., \digSumPeriodicNoJ^{|A_d|}) \neq 0$,
+we know that the shape must close.
+
+\subsubsection*{There does exist}
 

### 2022-05-10 old-frontend/public/build/bundle.js
mmm

@@ -3339,10 +3339,10 @@ var app = (function () {
             {
                 iterator: getRationalAngleIterator({
                     n: 7,
-                    d: 11,
-                    b: 4,
+                    d: 179,
+                    b: 19,
                 }),
-                base: 4,
+                base: 19,
                 usage: [
                     {
                         dimension: "X",
@@ -3362,7 +3362,7 @@ var app = (function () {
             {
                 iterator: getRationalAngleIterator({
                     n: 21,
-                    d: 11,
+                    d: 171,
                     b: 9,
                 }),
                 base: 9,

### 2022-05-10 old-frontend/src/store.ts

@@ -36,10 +36,10 @@ export const parameters: Writable<StoredParameters> = writable({
     {
       iterator: getRationalAngleIterator({
         n: 7,
-        d: 11,
-        b: 4,
+        d: 179,
+        b: 19,
       }),
-      base: 4,
+      base: 19,
       usage: [
         {
           dimension: "X",
@@ -59,7 +59,7 @@ export const parameters: Writable<StoredParameters> = writable({
     {
       iterator: getRationalAngleIterator({
         n: 21,
-        d: 11,
+        d: 171,
         b: 9,
       }),
       base: 9,

### 2022-05-11 paper/Paper.tex
complexity

--- 2022-05-09 paper/Paper.tex
@@
 \newcommand{\statePeriod}{T^j}
-\newcommand{\seedAngleJ}[2]{{\theta^{#2}_{#1}}}
-\newcommand{\seedAngle}[1]{{\theta^j_{#1}}}
-\newcommand{\seedAngleNotime}{{\theta}^j}
+\newcommand{\rationalAngleJ}[2]{{\theta^{#2}_{#1}}}
+\newcommand{\rationalAngle}[1]{{\theta^j_{#1}}}
+\newcommand{\rationalAngleNotime}{{\theta}^j}
 \newcommand{\state}[2]{{s_{#1}}^{#2}}
@@
 \newcommand{\inclIndic}[2]{{\mathrm{incl}_{#1}^{#2}}}
-\newcommand{\combSingleTerm}[1]{\prod_{j=1}^k \cos(\theta_j) ^ {\inclIndic{#1}{j}}}
-\newcommand{\digSumPeriodic}{\mathrm{digSumPeriodic}^j}
-\newcommand{\digSumPeriodicNoJ}{\mathrm{digSumPeriodic}}
+\newcommand{\numbToAngle}{\frac{2\pi}{b^j}}
+\newcommand{\numbToAngleNoJ}[1]{\frac{2\pi}{b^{#1}}}
+\newcommand{\combSingleTermCos}[1]{\prod_{j=1}^k \cos\left(\numbToAngle \cdot \theta^j\right) ^ {\inclIndic{#1}{j}}}
+\newcommand{\digSumPeriodic}{\sigma^j}
+\newcommand{\digSumPeriodicNoJ}{{\sigma}}
 \newcommand{\totalOverRationalFrac}{\frac{\totalPeriod}{\rationalPeriodTotal}}
+\newcommand{\changeTotalOneDim}{\Delta P_{0, T}^d}
+\newcommand{\digit}{\mathrm{digit}}
+\newcommand{\commonBase}{\pmb{b}}
+\newcommand{\numbToCommon}{\frac{\commonBase}{b^j}}
+\newcommand{\commonToAngle}{\frac{2\pi}{\commonBase}}
+\newcommand{\sinOrCos}{\phi^j}
+\newcommand{\combSingleTerm}[1]{\prod_{j=1}^k \sinOrCos\left(\numbToAngle \cdot \theta^j\right) ^ {\inclIndic{#1}{j}}}
 
@@
 
-Now say that the turtle's movement is determined by $k$ seed parameters drawn from
+Now say that the turtle's movement is determined by $k$ seed parameter drawn from
 the same set. Then, for some state space $\mathcal{S}$,
@@
 \subsection{Some more restrictions on our problem}
-We further restrict the problem by only considering the case where
+We further restrict the problem by only considering $\mathcal{S} = \N^4$ where for $(n, d, b, \theta) \in \mathcal{S}$,
+$n$ is the numerator of a rational in fraction form, $d$ is the denominator, 
+$b$ is the base (i.e.\ base 10, base 12, etc.),
+and $\frac{2\theta}{b \pi}$ is an ``angle" associated with the state.
+
+Then, let $\sinOrCos: \R \rightarrow \R$ equal $\cos$ or $\sin$.
+
+Now, we will only consider
+$$
+  SU_i^j(n, b, d, \theta) = (n, b, d, \theta + \mathrm{digit}(n, b, d, i) \mod b).
+$$
+where $\mathrm{digit}(n, b, d, i)$ gives us the $i$th digit of the decimal expansion of $\frac{n}{d}$
+in base $b$. For the sake of convenience, we will use the word ``rational parameter" 
+instead of ``seed parameter" from here on out.
+
+Moreover, we consider the case where
 $$
@@
 where $\mathrm{incl}_d^j \in \set{0, 1}$ for $d \in [D]$ indicates whether to include a given
-$x \in R$ determined by seed $j$ for position update in the $d$th dimension.
-
-We will also let $\mathcal{S} = N^5$ where for $(n, d, b, \theta) \in \mathcal{S}$,
-$n$ is the numerator of a rational in fraction form, $d$ is the denominator, 
-$b$ is the base (i.e\. base 10, base 12, etc.), $i$ is the current time step,
-and $\frac{2\theta}{b \pi}$ is an ``angle" associated with the state.
-Moreover, we will only consider
-$$
-  SU^j(n, b, d, \theta) = (n, b, d, \theta + \mathrm{digit}(n, b, d, i) \mod b).
-$$
-
-where $\mathrm{digit}(n, b, d, i)$ gives us the $i$th digit of the decimal expansion of $\frac{n}{d}$
-in base $b$.
+$x \in R$ determined by rational parameter $j$ for position update in the $d$th dimension.
 
@@
 
+Also, lets set 
+$$\commonBase = \lcm{(n, b, d, \theta) \in \pmb{s}_0} b.$$
+In other words,
+$\commonBase$ can be thought of as a ``common base" among all rational parameters.
+
 \subsubsection{Some intuition}
 While the restrictions may seem arbitrary, they aptly match our original problem statement.
-Take the three dimensional case with two seeds. The two seeds can be thought
-of as the fraction which generates the updates to two angles, $\theta, \alpha$.
-$\theta$ and $\alpha$ can then uniquely determine a direction in 3D space in which the 
-turtle is pointing. 
-So, at each time step $i + 1$, $\theta_{i + 1}$ equals to $\theta_i$, but rotated by
-some fraction of $2 \pi$ determined by the $i$th digit of the decimal expansion of one fraction and its base.
+The original problem statement derives a spherical change in position based off of a rational number's
+digit at a particular timestep. The polar change in position also has a fixed radius. Translating
+from a polar to cartesian update then only requires products of $\sin$s and $\cos$s. See \cite{NDimSphericalCoord}
+for more details.
+
+Take the three dimensional case for instance. The turtle's update cartesian space
+is given by 
+\begin{align*}
+  x &= \cos(\alpha)\\
+  y &= \sin(\alpha) \cos(\beta)\\
+  z &= \sin(\alpha) \sin(\beta)
+\end{align*}
+where $\alpha = \numbToAngleNoJ{1} \cdot \theta^1$ and 
+$\beta = \numbToAngleNoJ{2} \cdot \theta^2$. We can thus see that our definition
+of $\comb$ captures the three dimensional case.
+
 % TODO: clear up.
@@
 
-\section{Results}
+\section{Does it close?}
+In understanding whether a set of given rationals, bases, and updated functions 
+draw a closed shape in $D$ dimensional space, we first need to find the period of 
+the update delta, $\Delta p_i$. We then know that the total update over a period will be repeated 
+indefinitely. Consequently, we then seek to find the total change in position over a period. 
+If the total change is $0$, the shape will close as the Turtle will end up at its starting point
+after every period length. If the total update is nonzero, the Turtle will not draw a closed
+shape.
+
 \subsection{Finding period $T$}
@@
 
-\begin{remark}[Polytime]
-  TODO: remark about discrete log and similarity... (we think this is hard, but in QPP)...
+\begin{remark}[Complexity]
+  Interestingly, period finding of rational numbers is intimately tied to the discrete
+  log problem and factoring. For more information, check out \cite{MathOverflowFracPeriod}.
+  This gives some intuition that this closure problem may not be in BPP (Bounded Error Polynomial Time),
+  but may be in BQP (Bounded Error Quantum Polynomial Time) by \cite{Shor_1997}.
 \end{remark}
@@
 \begin{equation}
-  \digSumPeriodic = \sum_{i = i_0}^{i_0 + \rationalPeriodTotal} \mathrm{digit}(n, d, b, i)
+  \digSumPeriodic = \sum_{i = i_0}^{i_0 + \rationalPeriodTotal} \mathrm{digit}(n, d, b, i).
 \end{equation}
+In other words, $\rationalPeriodTotal$ is the digital sum over one period.
 
-\begin{remark}[Finding the digit sum of a rational]
-  aaaa
+\begin{remark}[Complexity]
+  For $d > 2$, prime, and coprime to $b$, we can find $\digSumPeriodic$
+  in polytime by multiplying $(b - 1) \cdot \frac{d-1}{2} \mod b$ \cite{OnDecSeq}. The authors are unsure
+  as to the complexity of finding $\digSumPeriodic$ otherwise.
 \end{remark}
 
-\subsubsection{Finding a period of $\seedAngleNotime$} % TODO: redifine things in terms of theta...
+\subsubsection{Finding a period of $\rationalAngleNotime$} % TODO: redifine things in terms of theta...
 For $(n^j, b^j, d^j, \theta_i^j) = s_i^j$,
-recall that $\seedAngle{i + 1} = \seedAngle{i} + \mathrm{digit}(n, b, d, i) \mod b$.
+recall that $\rationalAngle{i + 1} = \rationalAngle{i} + \mathrm{digit}(n, b, d, i) \mod b$.
 So, after period $\rationalPeriodTotal$,
@@
   \theta_{i + \rationalPeriodTotal} &= \left(\theta_{i} + \sum_{\ell = i}^{\rationalPeriodTotal + i} \mathrm{digit}(n, b, d, \ell)\right) \mod b\\
-  &= \left(\theta_{i} +  \digSumPeriodic\right) \mod b\\
-  &= \theta_{i} \mod b +  \digSumPeriodic \mod b.
+  &= \left(\theta_{i} +  \digSumPeriodic\right) \mod b.
 \end{align*}
@@
 $$
-\theta_{i + p\rationalPeriodTotal} = \theta_i.
+\theta_{i + p\rationalPeriodTotal} \equiv \theta_i + 0 \equiv \theta_i.
 $$
@@
 $$
-where $T^j$ is a period of the state for seed $j$.
+where $T^j$ is a period of the state for rational parameter $j$.
 % TODO: remove $i$ from the state and somehow have it be implicit....
@@
 
-\subsection{Does it close? $\Delta P_{i, i + T} = 0$?}
+\subsection{Finding the change in position over a period}
 So now that we know the period of $\totalStateNotime$, we can ask if
@@
 
-\subsubsection{Closing along a single dimension}
-Finally, to see if a shape will close,
-we just need to find if equation \eqref{eq:singleDelta0} holds true for all dimensions.
-First, let $A_d = \set{j \mid j \in [k] \; ; \inclIndic{d}{j} = 1}$
-We can then see that
-\begin{align*}
-&\sum_{i = 1}^T \combSingleTerm{d}\\
-&=\sum_{i = 1}^T \prod_{j = 1}^k \left(\half \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\right)^\inclIndic{d}{j}\\
-&=2^{-|A|} \sum_{i = 1}^T \prod_{j \in A_d} \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\\
-\end{align*}
-
-\newcommand{\periodFrac}{\frac{\totalPeriod}{\rationalPeriod}}
-\newcommand{\periodFracRational}{\frac{\rationalPeriodTotal}{\rationalPeriod}}
-
-We can then see that for $(n, b, d, \theta_i) \in \pmb{s}_i$ and $x, y \in \N$ where $y < \rationalPeriodTotal$,
-\begin{align}
-  \seedAngle{x \rationalPeriodTotal + y} &= \sum_{i = 0}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, i) \notag \\
-  &= \sum_{p = 0}^{(x- 1)\rationalPeriodTotal} \sum_{q=0}^{\rationalPeriodTotal - 1} \mathrm{digit}(n, b, d, p\rationalPeriodTotal + q)
-    + \sum_{p = x \rationalPeriodTotal}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, p) \notag \\
-    % ARGS::....
-  \label{eq:angleBreakdown}
-  &= x \cdot \digSumPeriodic + \sum_{p = x \rationalPeriodTotal}^{\rationalPeriodTotal + y}\mathrm{digit}(n, b, d, p) \notag \\
-  &= x \cdot \digSumPeriodic + \sum_{p = 0}^{y}\mathrm{digit}(n, b, d, p)
-\end{align}
-because $\mathrm{digit}(n, b, d, x\rationalPeriodTotal + \ell) = \mathrm{digit}(n, b, d, \ell)$ for any $\ell \in \N$
-by definition of periodicity.
-
-Observe that 
-\begin{align*}
- &\prod_{j \in A_d} \left(e^{\seedAngle{p \rationalPeriodTotal + q} I} +  e^{-\seedAngle{p \rationalPeriodTotal + q} I}\right) \\
- =& \exp(\seedAngleJ{p \rationalPeriodTotal + q}{1} + \seedAngleJ{p \rationalPeriodTotal + q}{2} + ... + \seedAngleJ{p \rationalPeriodTotal + q}{d}) 
-  + \exp(\seedAngleJ{p \rationalPeriodTotal + q}{1} - \seedAngleJ{p \rationalPeriodTotal + q}{2} + ... + \seedAngleJ{p \rationalPeriodTotal + q}{d}) + ... \\
-  &+ \exp(\seedAngleJ{p \rationalPeriodTotal + q}{1} - \seedAngleJ{p \rationalPeriodTotal + q}{2} - ... - \seedAngleJ{p \rationalPeriodTotal + q}{d})
-\end{align*}
-which then equals
-\begin{equation}
- \sum_{\beta \in \set{0,1}^{|A_d|}} 
-    \exp\left(
-        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-        \seedAngle{p \rationalPeriodTotal + q}I
-      \right).
-\end{equation}
-
+\begin{remark}[Complexity]
+  The algorithm we provide in equation \eqref{eq:singleDelta0} runs in time exponential 
+  in the size of the input assuming the Word RAM model. 
+  The period for the rational generated from rational parameter $j$, $1 \leq \rationalPeriod \leq d^j$. Then,
+  the period over all rationals generated from parameters is at most 
+  $$
+    \lcm{j \in [k]} \rationalPeriod \leq \prod_{j \in [k]} \rationalPeriod \leq \left(\max_{j \in [k]} \; d^j \right)^k.
+  $$
   Then, 
-\begin{align*}
- &2^{-|A|} \sum_{i = 1}^T \prod_{j \in A_d} \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\\
- =& 2^{-|A|} \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}\prod_{j \in A_d} \left(e^{\seedAngle{p \rationalPeriodTotal + q} I} +  e^{-\seedAngle{p \rationalPeriodTotal + q} I}\right)\\
- =&
-  2^{-|A|} \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
- \sum_{\beta \in \set{0,1}^{|A_d|}} 
-    \exp\left(
-        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-        \seedAngle{p \rationalPeriodTotal + q}I
-      \right)\\
- =&
-  2^{-|A|} 
- \sum_{\beta \in \set{0,1}^{|A_d|}} 
-     \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
-    \exp\left(
-        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-        \seedAngle{p \rationalPeriodTotal + q}I
-      \right).
-\end{align*}
-
-\newcommand{\eqWTSInnerProd}{
-  \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
-    \exp\left(
-        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-        \seedAngle{p \rationalPeriodTotal + q}I
-      \right)}
-
-Then, lets fix some $\beta \in \set{0, 1}^{|A_d|}$, we will now show that 
-\begin{equation}
-\label{eq:wts01}  
-  \eqWTSInnerProd
-\end{equation}
-always equals $0$ or $1$ for any choice of $\beta$.
-
-Observe that 
-\begin{align}
-  \exp(\seedAngle{p \rationalPeriodTotal + q}I) &= \exp\left(p \cdot \digSumPeriodic +
-    \sum_{\ell = p \rationalPeriodTotal}^{p \rationalPeriodTotal + q}\mathrm{digit}(n, b, d, \ell)\right) \tag{by equation \eqref{eq:angleBreakdown}} \\
-    \label{eq:expBreakdown}
-    &= \exp\left(p \cdot \digSumPeriodic\right) \exp\left(\sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)\right).
-\end{align}
-
-So then, by equation \eqref{eq:expBreakdown}, we get that
-\begin{align}
-&\exp\left(
-    \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-    \seedAngle{p \rationalPeriodTotal + q}I = 
-\right)\notag \\ 
-\label{eq:decomposeExp}
-=&
-\exp\left(
-    \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-    \cdot p \cdot
-    \digSumPeriodic
-\right)
-\exp\left(
-    \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-      \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell).
-\right).
-\end{align}
-
-We then use \eqref{eq:decomposeExp} to show that \eqref{eq:wts01} equals
-\begin{equation}
-\label{eq:inner-outer-split}
-  \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \left[
-    \exp\left(
-      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-      \digSumPeriodic
-    \right)
-  \left(
-  \sum_{q = 0}^{\rationalPeriodTotal - 1}
-    \exp\left(
-        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-          \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)
-    \right)\right)\right].
-\end{equation}
-
-\subsubsection*{Case 1}
-Observe that the inner sum,
-$
-  \sum_{q = 0}^{\rationalPeriodTotal - 1}
-  \exp\left(
-      \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-        \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)
-  \right)
-$,
-is invariant for all $p$ in equitation \eqref{eq:inner-outer-split}. So then,
-let the inner sum equal $C \in \Z$.  Moreover, note that 
-\begin{align*}
-  &\exp\left(
-      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-      \digSumPeriodic
-    \right)\\
-  =& \prod_{j \in A_d} \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right)
-\end{align*}
-and that 
-\begin{equation*}
-  \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right) = \exp\left(0\right) = 1
-\end{equation*}
-when $p = \frac{\totalPeriod}{\rationalPeriodTotal}$. Then, we can see that
+$0 \leq \totalPeriod \leq \rationalPeriodTotal \cdot \lcm{j \in [k]} b^j \leq \rationalPeriodTotal \left(\max_{j \in [k]} b^j\right)^k$.
+  And because evaluating the product in \eqref{eq:singleDelta0} takes $O(k)$ time,
+  we have that the time for \eqref{eq:singleDelta0} is at most
   $$
-\prod_{j \in A_d} \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right) = 1
+    O\left(\left[\max_{j \in [k]} \; (b^j d^j)\right]^k \right).
   $$
-when $p = \frac{\totalPeriod}{\rationalPeriodTotal}$.
-
-And so, because $\digSumPeriodic$ is a constant, we can conclude that
-\begin{equation*}
- \exp\left(
-      I \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-      \digSumPeriodic
-    \right) 
-\end{equation*}
-is a $\totalOverRationalFrac^th$ root of unity iff $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \neq 0$.
-
-So, for $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \neq 0$, we have that
-\begin{align*}
-  \eqWTSInnerProd &= C \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1}
-    \exp\left(
-      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-      \digSumPeriodic
-    \right) \\
-    &= C \sum_{p = 0}^{\totalOverRationalFrac - 1}\exp\left(W_{\totalOverRationalFrac}^p\right) \\
-    &= 0.
-\end{align*}
-where $W_{\totalOverRationalFrac}^p$ is the $\totalOverRationalFrac^{th}$ root of unity.
-
-If $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} = 0$, then 
-\begin{align*}
-  \eqWTSInnerProd &= C \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \exp(0) \\
-  &= 1.
-\end{align*}
-
-So, we have now shown that \eqref{eq:wts01} is always $0$ or $1$. In particular, we also have our first 
-closure result. If, $\forall \beta \in \set{0, 1}^{|A_d|}$, $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \neq 0$,
-\begin{align*}
-  \sum_{i = 1}^T \combSingleTerm{d} &=  2^{-|A|} 
-  \sum_{\beta \in \set{0,1}^{|A_d|}} 
-      \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
-     \exp\left(
-         \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
-         \seedAngle{p \rationalPeriodTotal + q}I
-       \right) \\
-        &= 0
-\end{align*}
-for all $d \in D$.
-So then, $\Delta P_{0, T} = 0$ whenever 
-no degree $1$ multinomials with coefficients of $-1$ or $1$ and $|A_d|$ variables has a root of $(\digSumPeriodicNoJ^1, \digSumPeriodicNoJ^2, ..., \digSumPeriodicNoJ^{|A_d|})$.
-In other words, if variables, $x_1 = \digSumPeriodicNoJ^1, x_2 = \digSumPeriodicNoJ^2, ...$, there does not exist a multinomial
-of form $\pm x_1 \pm x_2 \pm ... \pm x_{|A_d|} = 0$.
-
-% TODO: second part can be thought of as a constant for now... ie C2=
-% Then, we can think of the inner first sum as a constant of sorts, (C1)
-% And we know that pI(T/T') = 1 and that pI0 = 1. So, if C1 \neq 0, we get some roots of unity
-% and then the whole sum is 0...
-% If it does equal 0, you have to check if C2 = 0... don't really know how to do this...
-% If C1 = 0 and C2 not equal to 0, then
-
-% TODO: then think of notation for the "distributed" polynomial, then you can expand...
-% / assignment of +- strings... oy vey
-
-% TODO: no clue what is going on with C2... (maybe throw in some pictures...)
-
-% TODO: overall goal, show this is in coNP...
-
-% A bunch of sums and multiplies
-% \cite{watrous2018theory}
+  Because \eqref{eq:singleDelta0} must be computed for each dimension, the algorithm
+  runs in 
+  $$
+    O\left(D \left[\max_{j \in [k]} \; (b^j d^j)\right]^k \right)
+  $$
+  time.
+\end{remark}
 
@@
 \appendix
-\section{Finding the period of $\frac{n}{d}$}
+\section{Proving Property 1}
 \label{AppendixPeriod}
-aaaaa
+\include{PaperAppendix.tex}
 

### 2022-05-11 paper/Paper.tex
prog

@@
 \newcommand{\digit}{\mathrm{digit}}
-\newcommand{\commonBase}{\pmb{b}}
+\newcommand{\commonBase}{{\pmb{b}}}
 \newcommand{\numbToCommon}{\frac{\commonBase}{b^j}}
@@
 \end{equation}
-See, appendix \ref{AppendixPeriod} for more detail.
 More generally though, any nontrivial $\rationalPeriod$ satisfying equation \ref{eq:nd-period}
@@
 \begin{remark}[Complexity]
+\label{remark:periodcomplex}
   Interestingly, period finding of rational numbers is intimately tied to the discrete
@@
 for all $d \in D$.
+We can thus check for closure by computing \eqref{eq:singleDelta0} for each dimension.
 
-\begin{remark}[Complexity]
+\subsection{Algorithm complexity}
 The algorithm we provide in equation \eqref{eq:singleDelta0} runs in time exponential 
@@
 $$
+
+Then, note that computing the period of rational numbers via known classical methods takes 
+exponential time in the number of digits of the denominator. So, computing
+$\rationalPeriod$ takes $O(d^j)$ time. Then, computing the $\digSumPeriodic$
+can take $O(d^j)$ time. 
+We can thus see that period finding takes at most
+$$
+O\left(k \max_{j \in [k]} d^j \right)
+$$
+time.
+
 Because \eqref{eq:singleDelta0} must be computed for each dimension, the algorithm
@@
 $$
-    O\left(D \left[\max_{j \in [k]} \; (b^j d^j)\right]^k \right)
+  O\left(k \max_{j \in [k]} d^j \right) + 
+  O\left(\max_{j \in [k]} \; D (b^j d^j)^k \right) = 
+  O\left(\max_{j \in [k]} \; D (b^j d^j)^k \right)
 $$
 time.
+Note that $b^j, d^j$ are also exponential in the size of the input. 
+We can thus see that our running time is quite atrocious (its worse than exponential).
+Moreover, the algorithm does not produce a proof, verifiable in polytime, for closure 
+or lack there of. Thus, our algorithm is in neither NP or coNP.
+
+\section{Interesting Properties and an attempt at certificates}
+We will now proceed to go over some interesting properties of the closure question
+which may give rise to an algorithm in NP, coNP, or even BQP. These properties were discovered
+in the author's pursuit of simplifying the question. Moreover, these properties may guide
+some intuition as to the probability of closure for random rational seeds, a fixed $k$, 
+and fixed bases $b$.
+
+\subsection{Property 1: Restricted Monomials and Closure}
+Define $A_d = \set{j \mid j \in [k] \; \text{and}\; \inclIndic{d}{j} = 1}$, in other words,
+$A_d$ is the set of rational parameters which are included in determining the position along the $d$th dimension.
+Also, for function $f: \Z_\commonBase^{|A_d|} \rightarrow \Z_\commonBase$ and $\{a_1, a_2, ..., a_{|A_d|} \} = A_d$, we will denote
+$$
+  f\left(\digSumPeriodicNoJ^{a_1}, \digSumPeriodicNoJ^{a_2}, ..., \digSumPeriodicNoJ^{a_{A_d}}\right)
+  = f\left(\digSumPeriodicNoJ\right).
+$$
+
+Then, let
+$$
+\mathcal{M} = \{f : f(\pmb{x}) = \pm x_1 \pm x_2 ... \pm x_{|A_d|}\}.
+$$
+In other words, $\mathcal{M}$ is the set of all multinomials with $|A_d|$ variables with
+degree 1 and coefficients $\pm1$.
+Then,
+if \begin{equation}
+\label{eq:satisfy-multi}
+f\left(\digSumPeriodicNoJ\right) \neq 0
+\end{equation}
+for all $f \in \mathcal{M}$ and $d \in [D]$, the turtle will always draw a closed shape. See 
+Appendix \ref{appendix:prop1} for the proof.
+
+Satisfying \eqref{eq:satisfy-multi} is true for all $f$ is equivalent to
+$$
+  \prod_{f \in \mathcal{M}} f(\digSumPeriodicNoJ) \neq 0.
+$$
+
+where $\prod_{f \in \mathcal{M}} f$ is a polynomial of degree
+at most $2^{|A_d|} \leq 2^k$.
+
+If we were to then assume that $(\digSumPeriodicNoJ^1, ..., \digSumPeriodicNoJ^k)$ 
+is uniformly and randomly draw from $\Z_\commonBase^k$, we then know by the 
+Schwartz-Zippel Lemma
+$$
+  \Pr\left[\prod_{f \in \mathcal{M}} f(\digSumPeriodicNoJ) = 0\right] < \frac{2^k}{\commonBase}.
+$$
+% TODO: cite,
+So, this would leave us with
+$$
+  \Pr\left[\prod_{f \in \mathcal{M}} f(\digSumPeriodicNoJ) \neq 0\right] > 1 - \frac{2^k}{\commonBase}.
+$$
+In particular, this means that the probability of closure would be at least
+$$
+1 - \frac{2^k}{\commonBase}.
+$$
+
+\begin{remark}[Randomness assumption]
+  The randomness assumption, that $(\digSumPeriodicNoJ^1, ..., \digSumPeriodicNoJ^k)$
+  is drawn from a random distribution is very much not true. But, given a rational parameter
+  there does seem to be some element of randomness for $\digSumPeriodic$. See \cite{OnDecSeq} for more information.
 \end{remark}
-
 \section{Conclusion}
@@
 \section{Proving Property 1}
-\label{AppendixPeriod}
+\label{appendix:prop1}
 \include{PaperAppendix.tex}

### 2022-05-12 paper/Paper.tex
main proofs
intro and abstract

@@
 \pagebreak
+\section*{Abstract}
+Given an object in cartesian space, we ask whether a repeating sequence 
+of spherical updates to the object's position cause it to travel on a closed path.
+A spherical update to a position in $D$-dimensional space can be written as
+$\left(r, \theta_1, \theta_2, ..., \theta_{D-1}\right)$.
+In this paper, we consider $D-1$ non-terminating
+rational numbers where for time-step $i$, the spherical updates' difference function
+is given by $r' \leftarrow r$, 
+$\theta_1' \leftarrow \theta_1 + \mathrm{digit}(q_1, i)$, ..., 
+$\theta_{D-1}' \leftarrow \theta_{D-1} + \mathrm{digit}(q_{D-1}, i)$.
+We then proceed to derive a formula for finding if the object takes a closed, repeating path.
+Moreover, we explore interesting properties of this problem and
+relate it to discrete log, roots of a multinomial, and center of mass.
+
 \section{Introduction}
-- Numberphile video
-- I was bored and this looked fun
-- I wasn't paying attention in one of my lectures...
-- This paper is purely for funs... for now
+A glum Pittsburgh day inspired the authors to take a random walk down YouTube's recommended
+when they encountered the Numberphile video on ``Plotting Pi" \cite{NumberphileVid}.
+In the video, Henderson and Brady introduce the idea of taking a Python Turtle and
+deriving a series of updates to its position based off of various decimal sequences, 
+some rational, some irrational. More specifically, they place an object in 2D, cartesian
+space starting at $(0, 0)$ and ``facing" to the right. They then take a generating number, like $\pi$ or $35/99$, 
+which gives a decimal sequence ($3.14...$ and $0.\bar{35}$ respectively). 
+Then, at time step $i$, $i \geq 1$, they rotate the object by the $i$th digit divided by the base of
+the decimal sequence. Then, the Turtle moves a constant distance in the direction which it faces.
+For example, if the second digit is 4, the turtle is rotated by $\frac{4}{10}$ths of a circle
+counterclockwise at time step 2 and then moves 10 units in its new direction.
+% TODO: diagram, timestep 1 --> 2 --> 3
+
+Whenever the Turtle moves, the program draws a red line along the Turtle's path. Thus,
+different lines are drawn.
+The authors noticed that using rational numbers to generate the sequence often drew geometrically
+aesthetic, closed shapes.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=8cm]{fig/Turtle1D13Div113.png}
+  \caption{The closed shape generated from $\frac{13}{113} = 0.0977443609...$ in base $10$.}
+\end{figure}
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=8cm]{fig/Turtle1DNotClosed.png}
+  \caption{A non-closing shape generated from $\frac{2134}{9999} = 0.\overline{2134}$ in base $10$.}
+\end{figure}
+
+Naturally, the authors were curious whether a Turtle in ``3D" would also draw 
+aesthetic shapes. In other words, what if the Turtle's orientation was described
+by 2 angles, pitch and yaw. The pitch and yaw would then by independently updated
+by 2 decimal sequences generated from 2 rational numbers.
+% TODO: figure
+After writing the program, we noticed that the Turtle would often fail
+to close. In other words, the Turtle would go off in one direction forever.
+% TODO: picture of failing to close.
+But, the Turtle \textit{sometimes} closed.
+
+The authors then proceeded to ask why the Turtle would sometimes close and sometimes
+go off into the ether. After finding a closed form solution in 3 dimensional space,
+we proceeded to ask the same question in $D$ dimensional space: given $D - 1$ 
+rational decimal sequences which determine the Turtle's orientation in space,
+does the Turtle move in a closed shape (i.e.\ is the Turtle position always contained
+within some $D$ dimensional sphere off constant radius)?
 
@@
 
+Somewhat surprisingly, we can then see that probability of closure may increase exponentially
+with a decreasing $k$. Moreover, a larger $\commonBase$ also increases the lower bound!
+
 \begin{remark}[Randomness assumption]
@@
 \end{remark}
+\section{Open Questions}
+
 \section{Conclusion}
-
-\section{Open Questions}
 

### 2022-05-12 paper/Paper.tex
some questions

@@
 
-% TODO: ask closure question
-% TODO: show result that if $(s_{a}^1, ... ) = (s_{b}^1,...)$ then $b-a$ is a period for the state
-% and Delta p_a = p_b and is thus invariant under mod b-a. So, if Delta p_{b-a} \neq 0 
-% we have that the turtle will not move in a closed shape. If Delta p_{b-a} = 0, it will
-
 \subsection{Specifying the task ahead of us}
@@
 \begin{remark}[Complexity]
+\label{remark:digsum-complexity}
   For $d > 2$, prime, and coprime to $b$, we can find $\digSumPeriodic$
@@
 \begin{remark}[Randomness assumption]
+\label{remark:digSumRandomness}
   The randomness assumption, that $(\digSumPeriodicNoJ^1, ..., \digSumPeriodicNoJ^k)$
@@
 \end{remark}
-\section{Open Questions}
+
+\section{Open Questions and Future Work}
+A whole host of questions naturally arise from this problem. We will proceed to list
+the ones which immediately stand out. For a complete list of open problems, which have
+been solved, and the associated (financial) reward to each question, see our website
+::::TODO::::
+\begin{enumerate}
+  \item \textbf{Periodic Digit Sum in NP?}: As far as the authors are aware, given 
+  any rational number, $\frac{n}{d}$ in a fixed base $b$, is finding the sum of the digits in
+  one period modulo $b$ in $NP$? I.e. could one give a poly-size
+  certificate to a poly-time verifier which verifies if a digital sum equals $\sigma \in \Z_b$?
+  The size of the input is the number of bits required to describe $\frac{n}{d}$. The authors 
+  feel that intuitively the answer should be yes. A certificate could potentially be related
+  to the factors of the denominator and the period length. I.e.\ we know how to find
+  the periodic digital sum of a prime in polynomial time (see \ref{remark:digsum-complexity}). So,
+  could we somehow use this in combination with a prime factorization?
+
+  \item \textbf{Closure in NP or CoNP?}: For fixed bases of size $b$, is closure in NP of CoNP?
+  I.e.\ is there is a poly-sized certificate and poly-time verifier which can prove or disprove
+  that $D-1$ rationals draw a closed shape? The author's are uncertain here but conjecture
+  may be in CoNP. Either a gadget based reduction or a direct algorithm to generate a valid
+  certificate suffice to answer this question.
+
+  \item \textbf{Distribution }: Given a random rational number $\frac{n}{d}$
+  where $n \sim \Z_q$ and $d \sim \Z_q$ for some fixed $q \in \N$, what is the distribution
+  of $\sigma$, the periodic digital sum modulo base $b$? Specifically, is the distribution
+  indistinguishable (TODO: cite meaning) from the uniform distribution of $\Z_b$? 
+  See remark \ref{remark:digSumRandomness} for an application of this result.
+
+  \item \textbf{Decomposition}: This one is totally out of left field. From our analysis,
+  it seems as if using rational numbers to draw out shapes has a lot of underlying complexity
+  but also a lot of structure. The authors were wondering if given any closed shape $\ell$ which
+  can be described with $n$ bits, could poly-n bits be used in combination with the rational
+  sequence drawing algorithm described throughout this paper as description of $\ell$.
+  In other words, could some sort of ``Fourier Transform" be done between an explicitly described
+  closed shape and a sequence of rationals? We are also interested whether $1 - \epsilon$
+  approximation exists 
+  (where the approximation ``goodness" could be measured as a function of
+  average distance from the original line to the line generated via the sequence of rationals).
+
+\end{enumerate}
 

### 2022-05-12 paper/Paper.tex
last prop

@@
 \subsection{Finding period $T$}
-\subsubsection{Finding the period of $\frac{n}{d}$}
-We will first aim to find period $T$ of the state $\pmb{s}$.
-For some $(n, b, d, \theta) \in \pmb{s}_0$, by \cite{MathOverflowFracPeriod},
+We now show how to find a period $T$ of state $\pmb{s}$.
+
+\subsubsection{Finding the period of a fraction}
+For some $(n, b, d, \theta) \in \pmb{s}_0$,
 we have that the period of the decimal expansion of $\frac{n}{d}$
@@
 \label{eq:nd-period}
-b ^ {\rationalPeriod} \equiv 1 \mod d.
+b ^ {\rationalPeriod} \equiv 1 \mod d
 \end{equation}
+by \cite{MathOverflowFracPeriod}.
 More generally though, any nontrivial $\rationalPeriod$ satisfying equation \ref{eq:nd-period}
-will be a period of $\frac{n}{d}$.
+will be a period of $\frac{n}{d}$. In other words, the decimal sequence specified 
+by $\frac{n}{d}$ will repeat after every $\rationalPeriod$ steps for all digits 
+$n > n_0$ for some fixed $n_0$.
 
@@
 
-\subsection{Property 1: Restricted Monomials and Closure}
+\subsection{Property 1: Restricted Multinomials and Closure}
+\label{prop:1}
 Define $A_d = \set{j \mid j \in [k] \; \text{and}\; \inclIndic{d}{j} = 1}$, in other words,
@@
 If we were to then assume that $(\digSumPeriodicNoJ^1, ..., \digSumPeriodicNoJ^k)$ 
-is uniformly and randomly draw from $\Z_\commonBase^k$, we then know by the 
-Schwartz-Zippel Lemma
+is uniformly and randomly draw from $\Z_\commonBase^k$, we then know that
 $$
-  \Pr\left[\prod_{f \in \mathcal{M}} f(\digSumPeriodicNoJ) = 0\right] < \frac{2^k}{\commonBase}.
+  \Pr\left[\prod_{f \in \mathcal{M}} f(\digSumPeriodicNoJ) = 0\right] < \frac{2^k}{\commonBase}
 $$
-% TODO: cite,
+by the Schwartz-Zippel Lemma \cite{Shwartz} \cite{Zip}.
 So, this would leave us with
@@
 
+\subsection{Property 2: Root of Restricted Multinomial and Closure}
+First note that
+$$
+\mathcal{M} = \{f : f(\pmb{x}) = \pm x_1 \pm x_2 ... \pm x_{|A_d|}\} = 
+  \left\{\sum_{j \in |A_d|} (-1)^{\beta_j}\digSumPeriodic : \beta \in \set{0, 1}^{|A_d|} \right\}.
+$$
+Let $f_\beta \in \mathcal{M}$ then equal $\sum_{j \in |A_d|} (-1)^{\beta_j}\digSumPeriodic$.
+
+Then, let
+$$
+  \mathcal{B} = \left\{\beta: f_\beta(\sigma) = 0\right\}
+$$
+and $\overline{\mathcal{B}} = \mathcal{M} \setminus \mathcal{B}$. Then, if for all
+$\beta \in \mathcal{B}$,
+$$
+\sum_{q = 0}^{\rationalPeriodTotal - 1}
+  \exp\left(
+      I 
+      \commonToAngle 
+      \sum_{\ell = 0}^{q}
+      \sum_{j \in A_d}
+          \left(-1\right) ^ {\beta_{j}}
+          \numbToCommon
+          \mathrm{digit}(n, b, d, \ell)
+  \right) = 0
+$$
+the Turtle will draw a closed shape. While this may seem arbitrary, there is a unique
+and interesting geometric interpretation. 
+Let rational sequence $a_1, a_2, ..., a_{\rationalPeriodTotal}$ be equal to
+$
+\forall \ell \in [\rationalPeriodTotal]
+$,
+$$
+a_\ell = \sum_{j \in A_d}
+\left(-1\right) ^ {\beta_{j}}
+\numbToCommon
+\mathrm{digit}(n, b, d, \ell).
+$$
+In other words, we are creating a ``common" rational sequence by summing and subtracting
+our rational parameters in the least common multiple base $\commonBase$. Then,
+if $$
+\sum_{q = 0}^{\rationalPeriodTotal - 1}
+\exp\left(
+    I 
+    \commonToAngle 
+    \sum_{\ell = 0}^{q}
+      a_\ell
+  \right) = 0
+$$
+the Turtle closes. If $r_i = \commonToAngle \sum_{\ell = 0}^{q} a_\ell$ for 
+$i \in \set{0, ..., \rationalPeriodTotal - 1}$. Then $\exp(I \cdot r_i)$ can be thought of as some point around the 
+unit circle. Also, note that $r_{i + 1} = r_i + \commonToAngle a_{i+1}$. In otherwords,
+$r_i$ denotes some position around the complex unit circle where the subsequent updates
+to position are given by a sum and subtraction of rational parameters. Then, if the center of
+mass of these points around the unit circle is $0$, the Turtle draws a closed shape!
+The authors are unsure as to the underlying intuition for why this is true.
+
+% TODO: picture!!!!
+
+Over one common period for a all rational sequences, 
+$\rationalPeriodTotal$,
+
 \section{Open Questions and Future Work}
@@
 been solved, and the associated (financial) reward to each question, see our website
-::::TODO::::
 \begin{enumerate}
@@
   of $\sigma$, the periodic digital sum modulo base $b$? Specifically, is the distribution
-  indistinguishable (TODO: cite meaning) from the uniform distribution of $\Z_b$? 
+  indistinguishable \cite{barak_2097} from the uniform distribution of $\Z_b$? 
   See remark \ref{remark:digSumRandomness} for an application of this result.
@@
 
+  \item \textbf{Closure in BQP?}: Given that closure is intimately tied with period finding,
+  the authors wonder if this problem is in BQP (Bounded-error Quantum Polynomial Time). An algorithm
+  or existence result suffices.
+
+  \item \textbf{A different approach?}: Could a change in basis and/ or vector calculus be used (as a means of dealing 
+  with the change of basis from spherical coordinates to cartesian) to simplify the problem analysis?
+  The authors conjecture yes as all updates are in spherical coordinates but most of the paper's analysis
+  is done in cartesian space. But, it is not immediately obvious to the authors
+  how a change of basis could be applied.
+
 \end{enumerate}
@@
 
-\appendix
-\section{Proving Property 1}
-\label{appendix:prop1}
+\newpage
 \include{PaperAppendix.tex}
@@
 \end{document}
-
-% TODO: put b\theta / 2pi in State UPDATE

### 2022-05-13 paper/Paper.tex
fig

@@
 \newcommand{\numbToCommon}{\frac{\commonBase}{b^j}}
+\newcommand{\numbToCommonNoJ}[1]{\frac{\commonBase}{b^{#1}}}
 \newcommand{\commonToAngle}{\frac{2\pi}{\commonBase}}
@@
 counterclockwise at time step 2 and then moves 10 units in its new direction.
-% TODO: diagram, timestep 1 --> 2 --> 3
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=8cm]{fig/turtle2dtimestep.png}
+  \caption{The turtle moving according to decimal sequence $0.223$ in base $10$.}
+\end{figure}
 
@@
 
-\section{Background}
-- Digital math
-- Euler's formula
-- I payed attention in some of my lectures
+% \section{Background}
+% - Digital math
+% - Euler's formula
+% - I payed attention in some of my lectures
 
@@
 \subsection{The problem}
-Say we are given, $Comb$, hh$SU^j$, $p_0$, and $s^j_0$ for all $j \in [k]$.
+Say we are given, $Comb$, $SU^j$, $p_0$, and $s^j_0$ for all $j \in [k]$.
 Informally, the question is whether the turtle draws a ``closed" shape or not.\\
@@
 $$
-for $i, \ell \in \N$.
+for all $i, \ell \in \N$.
 Then, note that if there exists a period $T$ such that 
@@
 \subsection{Specifying the task ahead of us}
-For our case, we consider $Comb, SU_i^j$ to all be memoryless (i.e.\ there output
-is uniquely determined by the current input). So, we can simplify the overall question.
+For our case, we consider $Comb, SU_i^j$ to be uniquely determined by the current input.
+So, we can simplify the overall question.
 If, $\pmb{s}_i = \pmb{s}_{i + \ell T}$ for some $T \in \N$ and all $i \in \N$, then 
@@
 $$
-  f\left(\digSumPeriodicNoJ^{a_1}, \digSumPeriodicNoJ^{a_2}, ..., \digSumPeriodicNoJ^{a_{A_d}}\right)
+  f\left(\numbToCommonNoJ{a_1} \digSumPeriodicNoJ^{a_1}, \numbToCommonNoJ{a_2}\digSumPeriodicNoJ^{a_2}, ..., \numbToCommonNoJ{a_{A_d}}\digSumPeriodicNoJ^{a_{A_d}}\right)
   = f\left(\digSumPeriodicNoJ\right).
@@
 If we were to then assume that $(\digSumPeriodicNoJ^1, ..., \digSumPeriodicNoJ^k)$ 
-is uniformly and randomly draw from $\Z_\commonBase^k$, we then know that
+is uniformly and randomly draw from $\Z_\commonBase^k$ and $\commonBase$ is a prime, we then know that
 $$
@@
 \mathcal{M} = \{f : f(\pmb{x}) = \pm x_1 \pm x_2 ... \pm x_{|A_d|}\} = 
-  \left\{\sum_{j \in |A_d|} (-1)^{\beta_j}\digSumPeriodic : \beta \in \set{0, 1}^{|A_d|} \right\}.
+  \left\{\sum_{j \in |A_d|} (-1)^{\beta_j} \numbToCommon \digSumPeriodic : \beta \in \set{0, 1}^{|A_d|} \right\}.
 $$
-Let $f_\beta \in \mathcal{M}$ then equal $\sum_{j \in |A_d|} (-1)^{\beta_j}\digSumPeriodic$.
+Let $f_\beta \in \mathcal{M}$ then equal $\sum_{j \in |A_d|} (-1)^{\beta_j}\numbToCommon \digSumPeriodic$.
 
@@
 and interesting geometric interpretation. 
-Let rational sequence $a_1, a_2, ..., a_{\rationalPeriodTotal}$ be equal to
+Let a rational decimal sequence $a_1, a_2, ..., a_{\rationalPeriodTotal}$ be equal to
 $
@@
 $$
-the Turtle closes. If $r_i = \commonToAngle \sum_{\ell = 0}^{q} a_\ell$ for 
-$i \in \set{0, ..., \rationalPeriodTotal - 1}$. Then $\exp(I \cdot r_i)$ can be thought of as some point around the 
-unit circle. Also, note that $r_{i + 1} = r_i + \commonToAngle a_{i+1}$. In otherwords,
+the Turtle closes.
+If $r_i = \commonToAngle \sum_{\ell = 0}^{q} a_\ell$ for 
+$i \in \set{0, ..., \rationalPeriodTotal - 1}$, then $\exp(I \cdot r_i)$ can be thought of as some point at angle $r_i$ around the 
+complex unit circle. Also, note that $r_{i + 1} = r_i + \commonToAngle a_{i+1}$. In otherwords,
 $r_i$ denotes some position around the complex unit circle where the subsequent updates
-to position are given by a sum and subtraction of rational parameters. Then, if the center of
+to position are given the $a_i$s, which are a sum and subtraction of rational parameters. Then, if the center of
 mass of these points around the unit circle is $0$, the Turtle draws a closed shape!
@@
 % TODO: picture!!!!
-
-Over one common period for a all rational sequences, 
-$\rationalPeriodTotal$,
 
@@
 
-\section{Conclusion}
-
 \section*{Acknowledgments}
+The authors would like to thank their roommate Phu Nguyen for helping me work through the closure proofs
+as well as inspiring me to pursue this project. The authors would also like to thank C.J. Argue
+for assisting with the initial intuition and for providing encouragement. Moreover, the authors
+would like to acknowledge Shiva Peri for doing a fantastic job putting together the artistic aspects
+of the project as well as the website. Finally, the author would like to thank all their fantastic friends
+from college who inspired and encouraged them to pursue their interests.
 

### 2022-05-13 paper/Paper.tex
clean

@@
 Then, at time step $i$, $i \geq 1$, they rotate the object by the $i$th digit divided by the base of
-the decimal sequence. Then, the Turtle moves a constant distance in the direction which it faces.
+the decimal sequence. Then, the turtle moves a constant distance in the direction which it faces.
 For example, if the second digit is 4, the turtle is rotated by $\frac{4}{10}$ths of a circle
 counterclockwise at time step 2 and then moves 10 units in its new direction.
-\begin{figure}[ht]
+\begin{figure}[h]
   \centering
@@
 
-Whenever the Turtle moves, the program draws a red line along the Turtle's path. Thus,
+Whenever the turtle moves, the program draws a red line along the turtle's path. Thus,
 different lines are drawn.
@@
 
-\begin{figure}[ht]
+\begin{figure}[h]
   \centering
@@
 \end{figure}
-\begin{figure}[ht]
+\begin{figure}[h]
   \centering
@@
 Naturally, the authors were curious whether a Turtle in ``3D" would also draw 
-aesthetic shapes. In other words, what if the Turtle's orientation was described
+aesthetic shapes. In other words, what if the turtle's orientation was described
 by 2 angles, pitch and yaw. The pitch and yaw would then by independently updated
@@
 % TODO: figure
-After writing the program, we noticed that the Turtle would often fail
-to close. In other words, the Turtle would go off in one direction forever.
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=8cm]{fig/turtle.png}
+  \caption{The above is a placeholder, I would like to get Shiva to help me design a 3D graphic here}
+\end{figure}
+After writing the program, we noticed that the turtle would often fail
+to close. In other words, the turtle would go off in one direction forever.
 % TODO: picture of failing to close.
-But, the Turtle \textit{sometimes} closed.
+But, the turtle \textit{sometimes} closed.
 
-The authors then proceeded to ask why the Turtle would sometimes close and sometimes
+The authors then proceeded to ask why the turtle would sometimes close and sometimes
 go off into the ether. After finding a closed form solution in 3 dimensional space,
 we proceeded to ask the same question in $D$ dimensional space: given $D - 1$ 
-rational decimal sequences which determine the Turtle's orientation in space,
-does the Turtle move in a closed shape (i.e.\ is the Turtle position always contained
+rational decimal sequences which determine the turtle's orientation in space,
+does the turtle move in a closed shape (i.e.\ is the turtle position always contained
 within some $D$ dimensional sphere off constant radius)?
@@
 
+\pagebreak
 \section{Definitions and questions}
 \subsection{Definitions}
-Say you (yes you!) had a turtle living in $D$ dimensional Euclidean
+Say we had a turtle, Jimbo, living in $D$ dimensional Euclidean
 space and in discrete time. At time step $i$, where $i \in \Z$ and $i > 0$,
@@
 indefinitely. Consequently, we then seek to find the total change in position over a period. 
-If the total change is $0$, the shape will close as the Turtle will end up at its starting point
-after every period length. If the total update is nonzero, the Turtle will not draw a closed
+If the total change is $0$, the shape will close as the turtle will end up at its starting point
+after every period length. If the total update is nonzero, the turtle will not draw a closed
 shape.
@@
 $$
-the Turtle will draw a closed shape. While this may seem arbitrary, there is a unique
+the turtle will draw a closed shape. While this may seem arbitrary, there is a unique
 and interesting geometric interpretation. 
@@
 $$
-the Turtle closes.
+the turtle closes.
 If $r_i = \commonToAngle \sum_{\ell = 0}^{q} a_\ell$ for 
@@
 to position are given the $a_i$s, which are a sum and subtraction of rational parameters. Then, if the center of
-mass of these points around the unit circle is $0$, the Turtle draws a closed shape!
+mass of these points around the unit circle is $0$, the turtle draws a closed shape!
 The authors are unsure as to the underlying intuition for why this is true.

### 2022-05-13 paper/Paper.tex
clean up

@@
 \section*{Abstract}
-Given an object in cartesian space, we ask whether a repeating sequence 
-of spherical updates to the object's position cause it to travel on a closed path.
-A spherical update to a position in $D$-dimensional space can be written as
+Given an object in $D$ dimensional cartesian space, we ask whether a repeating sequence 
+of deltas to the object's position cause it to travel on a closed path.
+We consider deltas specified in a spherical basis which can be written as
 $\left(r, \theta_1, \theta_2, ..., \theta_{D-1}\right)$.
 In this paper, we consider $D-1$ non-terminating
-rational numbers where for time-step $i$, the spherical updates' difference function
-is given by $r' \leftarrow r$, 
+rational numbers where for time-step $i$, the deltas are given by $r' \leftarrow r$, 
 $\theta_1' \leftarrow \theta_1 + \mathrm{digit}(q_1, i)$, ..., 
@@
 \section{Introduction}
-A glum Pittsburgh day inspired the authors to take a random walk down YouTube's recommended
+A glum Pittsburgh day inspired the authors to take a random walk down YouTube's recommended section
 when they encountered the Numberphile video on ``Plotting Pi" \cite{NumberphileVid}.
@@
 space starting at $(0, 0)$ and ``facing" to the right. They then take a generating number, like $\pi$ or $35/99$, 
-which gives a decimal sequence ($3.14...$ and $0.\bar{35}$ respectively). 
+which gives a decimal sequence ($3.14...$ and $0.\overline{35}$ respectively). 
 Then, at time step $i$, $i \geq 1$, they rotate the object by the $i$th digit divided by the base of
@@
 counterclockwise at time step 2 and then moves 10 units in its new direction.
-\begin{figure}[h]
+\begin{figure}[h!]
   \centering
@@
 
-Whenever the turtle moves, the program draws a red line along the turtle's path. Thus,
-different lines are drawn.
+Whenever the turtle moves, the program draws a red line along the turtle's path.
 The authors noticed that using rational numbers to generate the sequence often drew geometrically
@@
 
-\begin{figure}[h]
+\begin{figure}[h!]
   \centering
   \includegraphics[width=8cm]{fig/Turtle1D13Div113.png}
-  \caption{The closed shape generated from $\frac{13}{113} = 0.0977443609...$ in base $10$.}
+  \caption{A closed 2D shape generated from $\frac{13}{113} = 0.0977443609...$ in base $10$.}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[h!]
   \centering
   \includegraphics[width=8cm]{fig/Turtle1DNotClosed.png}
-  \caption{A non-closing shape generated from $\frac{2134}{9999} = 0.\overline{2134}$ in base $10$.}
+  \caption{A non-closing 2D shape generated from $\frac{2134}{9999} = 0.\overline{2134}$ in base $10$.}
 \end{figure}
@@
 Naturally, the authors were curious whether a Turtle in ``3D" would also draw 
-aesthetic shapes. In other words, what if the turtle's orientation was described
+interesting paths. In other words, what if the turtle's orientation was described
 by 2 angles, pitch and yaw. The pitch and yaw would then by independently updated
@@
 % TODO: figure
-\begin{figure}[h]
+\begin{figure}[h!]
   \centering
   \includegraphics[width=8cm]{fig/turtle.png}
-  \caption{The above is a placeholder, I would like to get Shiva to help me design a 3D graphic here}
+  \caption{The above is a placeholder, I would like to get Shiva to help me design a 3D graphic here similar to Figure 1 but in 3D}
 \end{figure}
@@
 to close. In other words, the turtle would go off in one direction forever.
-% TODO: picture of failing to close.
+% TODO: picture of failing to close in 3d space
 But, the turtle \textit{sometimes} closed.
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=8cm]{fig/failclose3d.png}
+  \caption{A non closing 3D shape generated from $\frac{102}{999} = 0.\overline{102}$ and $\frac{223}{999} = 0.\overline{223}$ in base 10.}
+\end{figure}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=8cm]{fig/tempclose.jpeg}
+  \caption{A closing 3D shape generate from (?????... this is a placeholder).}
+\end{figure}
 
@@
 % - I payed attention in some of my lectures
+\pagebreak
 
-\pagebreak
 \section{Definitions and questions}
@@
 
-Now say that the turtle's movement is determined by $k$ seed parameter drawn from
-the same set. Then, for some state space $\mathcal{S}$,
+Now say that the turtle's movement is determined by $k$ parameter drawn from
+the same set, $\mathcal{P}$. Then, for some state space $\mathcal{S}$,
 define $s_i^j \in \mathcal{S}$ to be some arbitrary
-state associated with timestamp $i$ for the $j$th seed parameter where $j \in [k]$.
+state associated with time-step $i$ for the $j$th seed parameter where $j \in [k]$.
 Also, define $\pmb{s}_i = (s_i^1, s_i^2, ..., s_i^k)$.
@@
 $$
-In other words, $\Delta P_{a, b}$ is the change in position from timestep $a$ to $b$.
+In other words, $\Delta P_{a, b}$ is the change in position from time-step $a$ to $b$.
 
@@
 for all $i, \ell \in \N$.
-Then, note that if there exists a period $T$ such that 
+Then, note that iff there exists a period $T$ such that 
 $\Delta P_{i, i + \ell T} = 0$ for all $i, \ell \in N$, 
@@
 \subsection{Specifying the task ahead of us}
-For our case, we consider $Comb, SU_i^j$ to be uniquely determined by the current input.
+For our case, we consider $Comb, SU_i^j$ to be uniquely determined by the current state.
 So, we can simplify the overall question.
@@
 $n$ is the numerator of a rational in fraction form, $d$ is the denominator, 
-$b$ is the base (i.e.\ base 10, base 12, etc.),
-and $\frac{2\theta}{b \pi}$ is an ``angle" associated with the state.
+$b$ is the base,
+and $\frac{2 \pi \theta}{b}$ is an ``angle" associated with the state.
 
@@
 $$
-  Comb((., ., ., ., \theta^1), (., ., ., ., \theta^2), ..., (., ., ., ., \theta^k)) =
+  Comb((n^1, d^1, b^1, \theta^1), (n^2, b^2, b^2, \theta^2), ..., (n^k, d^k, b^k, \theta^k)) =
     \left(\combSingleTerm{1}, ..., \combSingleTerm{D}\right)
 $$
-where $\mathrm{incl}_d^j \in \set{0, 1}$ for $d \in [D]$ indicates whether to include a given
-$x \in R$ determined by rational parameter $j$ for position update in the $d$th dimension.
+where $\mathrm{incl}_d^j \in \set{0, 1}$ for $d \in [D]$ indicates whether to ``include" a
+rational parameter $j$ for position update in the $d$th dimension.
 
 Finally, for simplicity's sake, assume that $\theta = 0$ for all $(n, b, d, \theta) \in \pmb{s}_0$,
-$n < d$, and $\frac{n}{d}$'s decimal expansion is periodic after some $N \geq 0$ decimal places
-and does not terminate in base $b$.
+$n < d$, $\frac{n}{d}$'s decimal expansion is periodic after some $N \geq 0$ decimal places,
+and the decimal expansion does not terminate in base $b$.
 
@@
 The original problem statement derives a spherical change in position based off of a rational number's
-digit at a particular timestep. The polar change in position also has a fixed radius. Translating
-from a polar to cartesian update then only requires products of $\sin$s and $\cos$s. See \cite{NDimSphericalCoord}
+digit at a particular time-step. The spherical change in position also has a fixed radius. Translating
+from a spherical to cartesian update then only requires products of $\sin$'s and $\cos$'s. See \cite{NDimSphericalCoord}
 for more details.
@@
 
-\subsection{Finding period $T$}
+\subsection{Finding the state's period}
 We now show how to find a period $T$ of state $\pmb{s}$.
 
-\subsubsection{Finding the period of a fraction}
+\subsubsection{Finding the period of a decimal sequence}
 For some $(n, b, d, \theta) \in \pmb{s}_0$,
@@
 \subsubsection{Digital sum}
-Next, we introduce the idea digital sums.
+Next, we introduce the idea of digital sums.
 For some number $N \in \N$, $N$ can be represented in base $b$ via
@@
 \end{equation}
-In other words, $\rationalPeriodTotal$ is the digital sum over one period.
+In other words, $\digSumPeriodic$ is the digital sum over 
+a common decimal sequence period for all rational parameters.
 
@@
   For $d > 2$, prime, and coprime to $b$, we can find $\digSumPeriodic$
-  in polytime by multiplying $(b - 1) \cdot \frac{d-1}{2} \mod b$ \cite{OnDecSeq}. The authors are unsure
+  in polytime by multiplying $\frac{\commonBase}{b}(b - 1) \cdot \frac{d-1}{2} \mod b$ \cite{OnDecSeq}. The authors are unsure
   as to the complexity of finding $\digSumPeriodic$ otherwise.
@@
 
-\subsubsection{Finding a period of $\rationalAngleNotime$} % TODO: redifine things in terms of theta...
+\subsubsection{Finding a period of a parameter's state} % TODO: redifine things in terms of theta...
 For $(n^j, b^j, d^j, \theta_i^j) = s_i^j$,
@@
 $$
-For simplicity, lets define
+Now, lets define
 $$
@@
 where $T^j$ is a period of the state for rational parameter $j$.
-% TODO: remove $i$ from the state and somehow have it be implicit....
 
@@
 % and then have a sum for T
-\subsubsection{Finding the period of $\pmb{s}$}
+\subsubsection{Finding the period of the overall state}
 We can first see that for $\stateNotime{j} \in \pmb{s}$, $\stateNotime{j}$
-has period of $\statePeriod$. So, $\pmb{s}$ must have a period, $\totalPeriod$, of
+has period of $\statePeriod$. So, $\pmb{s}$ must have a period $\totalPeriod$ equaling
 $$
@@
 
-% TODO: cite https://math.stackexchange.com/questions/377683/length-of-period-of-decimal-expansion-of-a-fraction
-% TODO: formula in poly time
-% TODO: hmmm... specify i > n_0 (to get rid of initial stuff...)
-
-% https://en.wikipedia.org/wiki/Digital_root#:~:text=The%20digital%20root%20(also%20repeated,single%2Ddigit%20number%20is%20reached.
-
 \subsection{Finding the change in position over a period}
 So now that we know the period of $\totalStateNotime$, we can ask if
-$\Delta P_{i, i + T} = 0$. % TODO: reference
+$\Delta P_{i, i + T} = 0$.
 
@@
 
-\section{Interesting Properties and an attempt at certificates}
+\section{Interesting Properties}
 We will now proceed to go over some interesting properties of the closure question
@@
 \end{equation}
-for all $f \in \mathcal{M}$ and $d \in [D]$, the turtle will always draw a closed shape. See 
+for all $f \in \mathcal{M}$ and all dimensions, the turtle will always draw a closed shape. See 
 Appendix \ref{appendix:prop1} for the proof.
 
-Satisfying \eqref{eq:satisfy-multi} is true for all $f$ is equivalent to
+Then, satisfying \eqref{eq:satisfy-multi} for all $f$ in a dimension is equivalent to
 $$
@@
 $$
-  \mathcal{B} = \left\{\beta: f_\beta(\sigma) = 0\right\}
+  \mathcal{B} = \left\{\beta: f_\beta(\sigma) = 0\right\}.
 $$
-and $\overline{\mathcal{B}} = \mathcal{M} \setminus \mathcal{B}$. Then, if for all
+Then, if for all
 $\beta \in \mathcal{B}$,
@@
 In other words, we are creating a ``common" rational sequence by summing and subtracting
-our rational parameters in the least common multiple base $\commonBase$. Then,
+our rational parameters in base $\commonBase$. Then,
 if $$
@@
 
-% TODO: picture!!!!
+For example, say that rational parameters $\frac{22,022}{99,999} = 0.\overline{22022}$ and
+$\frac{200}{99,999} = 0.\overline{00200}$ determine the movement in the $x$, $y$, and $z$ axis for $3$ dimensions.
+Then, $\sigma^1 = 8$ and $\sigma^2 = 2$. Also note that we are in base 10 so $b^1 = b^2 = \commonBase = 10$.
+Also, $f_{00}(8, 2) = 8 + 2 = 10 \equiv 0 \mod 10$. But then, we have that $a = 0.\overline{22222}$.
+So then, the ``movement" around the unit circle ends up being evenly spaced out and the center of mass
+is 0. Thus, we know that the turtle will close.
 
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=8cm]{fig/evenspacing.png}
+  \caption{If $a = 0.\overline{22222}$, then $r_1, ..., r_5$ are spaced around the unit circle as shown in the figure. We can thus
+  see that the center of mass is 0.}
+
+\end{figure}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=8cm]{fig/3DTurtleCenterOfMass.png}
+  \caption{The turtle moving according to rationals $\frac{22,022}{99,999}$ and $\frac{200}{99,999}$.}
+\end{figure}
+
+\pagebreak
 \section{Open Questions and Future Work}
@@
   feel that intuitively the answer should be yes. A certificate could potentially be related
-  to the factors of the denominator and the period length. I.e.\ we know how to find
+  to the prime factors of the denominator and the period length. I.e.\ we know how to find
   the periodic digital sum of a prime in polynomial time (see \ref{remark:digsum-complexity}). So,
@@
   that $D-1$ rationals draw a closed shape? The author's are uncertain here but conjecture
-  may be in CoNP. Either a gadget based reduction or a direct algorithm to generate a valid
-  certificate suffice to answer this question.
+  may be in CoNP.
 
@@
   approximation exists 
-  (where the approximation ``goodness" could be measured as a function of
+  (where the approximation factor could be measured as a function of
   average distance from the original line to the line generated via the sequence of rationals).
@@
   \item \textbf{Closure in BQP?}: Given that closure is intimately tied with period finding,
-  the authors wonder if this problem is in BQP (Bounded-error Quantum Polynomial Time). An algorithm
-  or existence result suffices.
+  the authors wonder if this problem is in BQP (Bounded-error Quantum Polynomial Time).
 
@@
 \section*{Acknowledgments}
-The authors would like to thank their roommate Phu Nguyen for helping me work through the closure proofs
-as well as inspiring me to pursue this project. The authors would also like to thank C.J. Argue
+The authors would like to thank their roommate Phu Nguyen for helping them work through the closure proofs
+as well as inspiring them to pursue this project. The authors would also like to thank C.J. Argue
 for assisting with the initial intuition and for providing encouragement. Moreover, the authors
 would like to acknowledge Shiva Peri for doing a fantastic job putting together the artistic aspects
-of the project as well as the website. Finally, the author would like to thank all their fantastic friends
-from college who inspired and encouraged them to pursue their interests.
+of the project as well as the website. Finally, the author would like to thank all their friends
+who encouraged them to pursue their interests.
 

### 2022-05-13 paper/Paper.tex
CLEAN COMPLEX

@@
 \subsection{Algorithm complexity}
-The algorithm we provide in equation \eqref{eq:singleDelta0} runs in time exponential 
+The algorithm we provide in equation \eqref{eq:singleDelta0} runs in worse than exponential time
 in the size of the input assuming the Word RAM model. 
@@
 exponential time in the number of digits of the denominator. So, computing
-$\rationalPeriod$ takes $O(d^j)$ time. Then, computing the $\digSumPeriodic$
+$\rationalPeriod$ takes $\widetilde{O}(d^j)$ time. Then, computing the $\digSumPeriodic$
 can take $O(d^j)$ time. 
@@
 $$
-O\left(k \max_{j \in [k]} d^j \right)
+\widetilde{O}\left(k \max_{j \in [k]} d^j \right)
 $$
@@
 $$
-  O\left(k \max_{j \in [k]} d^j \right) + 
+  \widetilde{O}\left(k \max_{j \in [k]} d^j \right) + 
   O\left(\max_{j \in [k]} \; D (b^j d^j)^k \right) = 
-  O\left(\max_{j \in [k]} \; D (b^j d^j)^k \right)
+  \widetilde{O}\left(\max_{j \in [k]} \; D (b^j d^j)^k \right)
 $$

### 2022-05-15 paper/Paper.tex
fix up notation

@@
 \newcommand{\combSingleTermCos}[1]{\prod_{j=1}^k \cos\left(\numbToAngle \cdot \theta^j\right) ^ {\inclIndic{#1}{j}}}
-\newcommand{\digSumPeriodic}{\sigma^j}
-\newcommand{\digSumPeriodicNoJ}{{\sigma}}
 \newcommand{\totalOverRationalFrac}{\frac{\totalPeriod}{\rationalPeriodTotal}}
@@
 \newcommand{\combSingleTerm}[1]{\prod_{j=1}^k \sinOrCos\left(\numbToAngle \cdot \theta^j\right) ^ {\inclIndic{#1}{j}}}
+\newcommand{\digSumPeriodic}{\sigma^j}
+\newcommand{\digSumPeriodicNoJ}{{\sigma}}
 
@@
 
-Moreover, define $\digSumPeriodic \in \Z_b$
+Moreover, for the $j$th rational parameter define $\digSumPeriodic \in \Z_{\commonBase}$
 such that
@@
 \begin{equation}
-  \digSumPeriodic = \sum_{i = i_0}^{i_0 + \rationalPeriodTotal} \mathrm{digit}(n, d, b, i).
+  \digSumPeriodic = \numbToCommon \sum_{i = i_0}^{i_0 + \rationalPeriodTotal} \mathrm{digit}(n^j, d^j, b^j, i).
 \end{equation}
-In other words, $\digSumPeriodic$ is the digital sum over 
+In other words, $\digSumPeriodic$ is the ``normalized" digital sum over 
 a common decimal sequence period for all rational parameters.
@@
 $$
-  f\left(\numbToCommonNoJ{a_1} \digSumPeriodicNoJ^{a_1}, \numbToCommonNoJ{a_2}\digSumPeriodicNoJ^{a_2}, ..., \numbToCommonNoJ{a_{A_d}}\digSumPeriodicNoJ^{a_{A_d}}\right)
+  f\left(\digSumPeriodicNoJ^{a_1}, \digSumPeriodicNoJ^{a_2}, ..., \digSumPeriodicNoJ^{a_{A_d}}\right)
   = f\left(\digSumPeriodicNoJ\right).
@@
 \mathcal{M} = \{f : f(\pmb{x}) = \pm x_1 \pm x_2 ... \pm x_{|A_d|}\} = 
-  \left\{\sum_{j \in |A_d|} (-1)^{\beta_j} \numbToCommon \digSumPeriodic : \beta \in \set{0, 1}^{|A_d|} \right\}.
+  \left\{\sum_{j \in |A_d|} (-1)^{\beta_j} \digSumPeriodic : \beta \in \set{0, 1}^{|A_d|} \right\}.
 $$
@@
           \left(-1\right) ^ {\beta_{j}}
-          \numbToCommon
           \mathrm{digit}(n, b, d, \ell)
@@
 Then, $\sigma^1 = 8$ and $\sigma^2 = 2$. Also note that we are in base 10 so $b^1 = b^2 = \commonBase = 10$.
-Also, $f_{00}(8, 2) = 8 + 2 = 10 \equiv 0 \mod 10$. But then, we have that $a = 0.\overline{22222}$.
+So, $f_{00}(8, 2) = 8 + 2 = 10 \equiv 0 \mod 10$. But then, we have that $a = 0.\overline{22222}$.
 So then, the ``movement" around the unit circle ends up being evenly spaced out and the center of mass

### 2022-09-04 frontend/src/config.ts
readme and clean up

@@ -1,0 +1,59 @@
+export const CONTRACT_NAME = process.env.CONTRACT_NAME || 'dev-1662325086933-22243500283897';
+
+export function getConfig(env) {
+  switch(env) {
+    case 'mainnet':
+      return {
+        networkId: 'mainnet',
+        nodeUrl: 'https://rpc.mainnet.near.org',
+        contractName: CONTRACT_NAME,
+        walletUrl: 'https://wallet.near.org',
+        helperUrl: 'https://helper.mainnet.near.org'
+      };
+    // This is an example app so production is set to testnet.
+    // You can move production to mainnet if that is applicable.
+    case 'production':
+    case 'development':
+    case 'testnet':
+      return {
+        networkId: 'testnet',
+        nodeUrl: 'https://rpc.testnet.near.org',
+        contractName: CONTRACT_NAME,
+        walletUrl: 'https://wallet.testnet.near.org',
+        helperUrl: 'https://helper.testnet.near.org'
+      };
+    case 'betanet':
+      return {
+        networkId: 'betanet',
+        nodeUrl: 'https://rpc.betanet.near.org',
+        contractName: CONTRACT_NAME,
+        walletUrl: 'https://wallet.betanet.near.org',
+        helperUrl: 'https://helper.betanet.near.org'
+      };
+    case 'local':
+      return {
+        networkId: 'local',
+        nodeUrl: 'http://localhost:3030',
+        keyPath: `${process.env.HOME}/.near/validator_key.json`,
+        walletUrl: 'http://localhost:4000/wallet',
+        contractName: CONTRACT_NAME
+      };
+    case 'test':
+    case 'ci':
+      return {
+        networkId: 'shared-test',
+        nodeUrl: 'https://rpc.ci-testnet.near.org',
+        contractName: CONTRACT_NAME,
+        masterAccount: 'test.near'
+      };
+    case 'ci-betanet':
+      return {
+        networkId: 'shared-test-staging',
+        nodeUrl: 'https://rpc.ci-betanet.near.org',
+        contractName: CONTRACT_NAME,
+        masterAccount: 'test.near'
+      };
+    default:
+      throw Error(`Unconfigured environment '${env}'. Can be configured in src/config.js.`);
+  }
+}

### 2022-09-04 frontend/src/near.ts

@@ -1,0 +1,78 @@
+import * as nearAPI from "near-api-js";
+import { Contract, utils } from "near-api-js";
+import { CONTRACT_NAME, getConfig } from "./config";
+import type { Rational } from "./interfaces";
+
+// create a keyStore for signing transactions using the user's key
+// which is located in the browser local storage after user logs in
+const keyStore = new nearAPI.keyStores.BrowserLocalStorageKeyStore();
+const env = "testnet";
+
+const nearConfig = {
+  keyStore,
+  ...getConfig(env),
+};
+
+// Initializing connection to the NEAR testnet
+const near = await nearAPI.connect(nearConfig);
+
+// Initialize wallet connection
+export const walletConnection = new nearAPI.WalletConnection(near, null);
+
+const getContract = (): nearAPI.Contract => {
+  const account = walletConnection.account();
+  const contract = new Contract(account, CONTRACT_NAME, {
+    // name of contract you're connecting to
+    viewMethods: ["nft_minted"], // view methods do not change state but usually return a value
+    changeMethods: ["nft_mint"], // change methods modify state
+  });
+  return contract;
+};
+
+const MINT_AMOUNT = 10;
+
+export const mint = async (
+  r1: Rational,
+  r2: Rational,
+  thickness: number,
+  speed: number
+): Promise<void> => {
+  //@ts-ignore
+  await getContract().nft_mint(
+    {
+      r1,
+      r2,
+      receiver_id: walletConnection.getAccountId(),
+      thickness,
+      speed,
+    },
+    "300000000000000", // attached GAS (optional)
+    (
+      BigInt(MINT_AMOUNT) + BigInt(utils.format.parseNearAmount("0.1"))
+    ).toString()
+  );
+};
+
+export const checkMinted = async (
+  r1: Rational,
+  r2: Rational
+): Promise<boolean> => {
+  //@ts-ignore
+  const response = await getContract().nft_minted({
+    r1,
+    r2,
+  });
+  return response;
+};
+
+export const signIn = () => {
+  walletConnection.requestSignIn({
+    contractId: nearConfig.contractName,
+  });
+  // TODO: method names
+};
+
+export const signOut = () => {
+  walletConnection.signOut();
+  window.location.reload();
+};

### 2022-09-04 frontend/vite.config.ts

@@ -1,7 +1,31 @@
-import { defineConfig } from 'vite'
-import { svelte } from '@sveltejs/vite-plugin-svelte'
+import { defineConfig } from "vite";
+import resolve from "rollup-plugin-node-resolve";
+import { svelte } from "@sveltejs/vite-plugin-svelte";
+import { NodeGlobalsPolyfillPlugin } from "@esbuild-plugins/node-globals-polyfill";
 
 // https://vitejs.dev/config/
 export default defineConfig({
-  plugins: [svelte()]
-})
+  // resolve: {
+  //   fallback: {
+  //     buffer: require.resolve("buffer/"),
+  //   },
+  // },
+  define: {
+    "process.env": {},
+  },
+  optimizeDeps: {
+    esbuildOptions: {
+      // Node.js global to browser globalThis
+      define: {
+        global: "globalThis",
+      },
+      // Enable esbuild polyfill plugins
+      plugins: [
+        NodeGlobalsPolyfillPlugin({
+          buffer: true,
+        }),
+      ],
+    },
+  },
+  plugins: [svelte()],
+});

### 2022-09-04 nft/src/lib.rs
readme

@@ -15,17 +15,20 @@ NOTES:
   - To prevent the deployed contract from being modified or deleted, it should not have any access
     keys on its account.
 */
+use std::convert::TryFrom;
+
 use near_contract_standards::non_fungible_token::metadata::{
     NFTContractMetadata, NonFungibleTokenMetadataProvider, TokenMetadata, NFT_METADATA_SPEC,
 };
 use near_contract_standards::non_fungible_token::NonFungibleToken;
 use near_contract_standards::non_fungible_token::{Token, TokenId};
 use near_sdk::borsh::{self, BorshDeserialize, BorshSerialize};
-use near_sdk::collections::{LazyOption, LookupSet};
+use near_sdk::collections::{LazyOption, LookupSet, UnorderedSet};
+use near_sdk::env::promise_batch_action_add_key_with_full_access;
 use near_sdk::json_types::ValidAccountId;
 use near_sdk::serde::{Deserialize, Serialize};
 use near_sdk::{
-    env, near_bindgen, AccountId, BorshStorageKey, PanicOnDefault, Promise, PromiseOrValue,
+    env, near_bindgen, AccountId, Balance, BorshStorageKey, PanicOnDefault, Promise, PromiseOrValue,
 };
 
 near_sdk::setup_alloc!();
@@ -49,7 +52,7 @@ pub struct Contract {
     /// The maximum number of NFTs to be minted
     max_supply: u32,
     /// The price (in whole Near) for each NFT
-    mint_price: u32,
+    mint_price: Balance,
     /// Keep track of the minted rational pairs
     minted_rational_pairs: LookupSet<(Rational, Rational)>,
     /// base media URL:
@@ -70,21 +73,21 @@ enum StorageKey {
 #[near_bindgen]
 impl Contract {
     #[init]
-    pub fn new_default_meta(owner_id: ValidAccountId) -> Self {
+    pub fn new_default_meta() -> Self {
         Self::new(
-            owner_id,
+            ValidAccountId::try_from(env::predecessor_account_id()).unwrap(),
             NFTContractMetadata {
                 spec: NFT_METADATA_SPEC.to_string(),
-                name: "Example NEAR non-fungible token".to_string(),
-                symbol: "EXAMPLE".to_string(),
-                icon: Some(DATA_IMAGE_SVG_NEAR_ICON.to_string()),
+                name: "3D Turles".to_string(),
+                symbol: "3DTURT".to_string(),
[…]

### 2022-09-04 frontend/src/near.ts
fix bug

@@ -1,5 +1,6 @@
 import * as nearAPI from "near-api-js";
-import { Contract, utils } from "near-api-js";
+import { Contract, Near, utils } from "near-api-js";
+import { writable, type Writable } from "svelte/store";
 import { CONTRACT_NAME, getConfig } from "./config";
 import type { Rational } from "./interfaces";
 
@@ -13,14 +14,22 @@ const nearConfig = {
   ...getConfig(env),
 };
 
+export const near: Writable<Near | null> = writable(null);
+
+export const setNear = async () => {
+  const _near = await nearAPI.connect(nearConfig);
+  console.log("AA", _near)
+  near.set(_near);
+};
+
+export const getWalletConnection = (near: Near) => {
+  return new nearAPI.WalletConnection(near, null);
+};
 // Initializing connection to the NEAR testnet
-const near = await nearAPI.connect(nearConfig);
+// const near =
 
-// Initialize wallet connection
-export const walletConnection = new nearAPI.WalletConnection(near, null);
-
-const getContract = (): nearAPI.Contract => {
-  const account = walletConnection.account();
+const getContract = (near: Near): nearAPI.Contract => {
+  const account = getWalletConnection(near).account();
   const contract = new Contract(account, CONTRACT_NAME, {
     // name of contract you're connecting to
     viewMethods: ["nft_minted"], // view methods do not change state but usually return a value
@@ -32,17 +41,18 @@ const getContract = (): nearAPI.Contract => {
 const MINT_AMOUNT = 10;
 
 export const mint = async (
+  near: Near,
   r1: Rational,
   r2: Rational,
   thickness: number,
   speed: number
 ): Promise<void> => {
   //@ts-ignore
-  await getContract().nft_mint(
+  await getContract(near).nft_mint(
     {
       r1,
       r2,
-      receiver_id: walletConnection.getAccountId(),
+      receiver_id: getWalletConnection(near).getAccountId(),
       thickness,
       speed,
     },
@@ -58,21 +68,21 @@ export const checkMinted = async (
   r2: Rational
 ): Promise<boolean> => {
   //@ts-ignore
-  const response = await getContract().nft_minted({
+  const response = await getContract(near).nft_minted({
     r1,
     r2,
   });
   return response;
 };
 
-export const signIn = () => {
-  walletConnection.requestSignIn({
+export const signIn = (near: Near) => {
+  getWalletConnection(near).requestSignIn({
     contractId: nearConfig.contractName,
   });
[…]

### 2022-09-05 frontend/src/main.ts
near works

@@ -1,7 +1,11 @@
-import App from './App.svelte'
+import App from "./App.svelte";
 
+import * as buffer from "buffer";
+// issue of near-api-js
+// https://github.com/near/near-api-js/issues/757
+(window as any).Buffer = buffer.Buffer;
 const app = new App({
-  target: document.getElementById('app')
-})
+  target: document.getElementById("app"),
+});
 
-export default app
+export default app;

### 2022-09-05 frontend/src/near.ts

@@ -1,29 +1,34 @@
-import * as nearAPI from "near-api-js";
-import { Contract, Near, utils } from "near-api-js";
+import "near-api-js/dist/near-api-js";
+import type { Contract, Near, utils } from "near-api-js";
 import { writable, type Writable } from "svelte/store";
 import { CONTRACT_NAME, getConfig } from "./config";
 import type { Rational } from "./interfaces";
 
+//@ts-ignore
+const nearAPI = window.nearApi
+
 // create a keyStore for signing transactions using the user's key
 // which is located in the browser local storage after user logs in
-const keyStore = new nearAPI.keyStores.BrowserLocalStorageKeyStore();
+let keyStore;
 const env = "testnet";
 
-const nearConfig = {
-  keyStore,
-  ...getConfig(env),
-};
+let nearConfig;
 
 export const near: Writable<Near | null> = writable(null);
 
 export const setNear = async () => {
+  console.log(nearAPI, nearAPI.keyStores)
+  keyStore = new nearAPI.keyStores.BrowserLocalStorageKeyStore();
+  nearConfig = {
+    keyStore,
+    ...getConfig(env),
+  };
   const _near = await nearAPI.connect(nearConfig);
-  console.log("AA", _near)
   near.set(_near);
 };
 
 export const getWalletConnection = (near: Near) => {
-  return new nearAPI.WalletConnection(near, null);
+  return new nearAPI.WalletConnection(near, "3D Turtle");
 };
 // Initializing connection to the NEAR testnet
 // const near =

### 2022-09-05 frontend/vite.config.ts

@@ -2,14 +2,12 @@ import { defineConfig } from "vite";
 import resolve from "rollup-plugin-node-resolve";
 import { svelte } from "@sveltejs/vite-plugin-svelte";
 import { NodeGlobalsPolyfillPlugin } from "@esbuild-plugins/node-globals-polyfill";
+import { viteCommonjs } from "@originjs/vite-plugin-commonjs";
+import babel from "@rollup/plugin-babel";
+import legacy from "@vitejs/plugin-legacy";
 
 // https://vitejs.dev/config/
 export default defineConfig({
-  // resolve: {
-  //   fallback: {
-  //     buffer: require.resolve("buffer/"),
-  //   },
-  // },
   define: {
     "process.env": {},
   },
@@ -20,11 +18,6 @@ export default defineConfig({
         global: "globalThis",
       },
       // Enable esbuild polyfill plugins
-      plugins: [
-        NodeGlobalsPolyfillPlugin({
-          buffer: true,
-        }),
-      ],
     },
   },
   plugins: [svelte()],

### 2022-09-06 frontend/src/near.ts
clean

@@ -33,9 +33,9 @@ export const getWalletConnection = (near: Near) => {
 // Initializing connection to the NEAR testnet
 // const near =
 
-const getContract = (near: Near): nearAPI.Contract => {
+const getContract = (near: Near): Contract => {
   const account = getWalletConnection(near).account();
-  const contract = new Contract(account, CONTRACT_NAME, {
+  const contract = new nearAPI.Contract(account, CONTRACT_NAME, {
     // name of contract you're connecting to
     viewMethods: ["nft_minted"], // view methods do not change state but usually return a value
     changeMethods: ["nft_mint"], // change methods modify state
@@ -63,7 +63,7 @@ export const mint = async (
     },
     "300000000000000", // attached GAS (optional)
     (
-      BigInt(MINT_AMOUNT) + BigInt(utils.format.parseNearAmount("0.1"))
+      BigInt(MINT_AMOUNT) + BigInt(nearAPI.utils.format.parseNearAmount("0.1"))
     ).toString()
   );
 };

### 2022-09-06 frontend/src/store.ts
clean

@@ -117,7 +117,7 @@ export const setParams = () => {
 		parameters.set(generateParams(yaw, pitch, distance));
 	} catch (e) {
 		controlParams.update((p) => {
-			return { ...p, allowControls: true, displayPreview: true };
+			return { ...p, numStepsPerLoop: p.numStepsPerLoop ?? 1, pathWidth: p.pathWidth ?? 0.5, allowControls: true, displayPreview: true };
 		});
 		console.log('Could not parse URL params using defaults', e);
 	}

### 2022-09-06 frontend/src/store.ts
clean

@@ -117,7 +117,7 @@ export const setParams = () => {
 		parameters.set(generateParams(yaw, pitch, distance));
 	} catch (e) {
 		controlParams.update((p) => {
-			return { ...p, numStepsPerLoop: p.numStepsPerLoop ?? 1, pathWidth: p.pathWidth ?? 0.5, allowControls: true, displayPreview: true };
+			return { ...p, allowControls: true, displayPreview: true };
 		});
 		console.log('Could not parse URL params using defaults', e);
 	}

### 2022-09-18 integration-tests/ts/src/main.ava.ts
update to 4.0 and update tests to work

@@ -1,0 +1,797 @@
+import {
+  Worker,
+  NearAccount,
+  tGas,
+  NEAR,
+  BN,
+  ChildProcessPromise,
+} from "near-workspaces";
+import anyTest, { TestFn } from "ava";
+import { mint_more, nft_total_supply } from "./utils";
+
+const DEFAULT_MAX_SUPPLY = 10;
+
+const test = anyTest as TestFn<{
+  worker: Worker;
+  accounts: Record<string, NearAccount>;
+}>;
+
+test.beforeEach(async (t) => {
+  const worker = await Worker.init();
+  const root = worker.rootAccount;
+  const nft = await root.devDeploy("../../res/non_fungible_token.wasm", {
+    initialBalance: NEAR.parse("100 N").toJSON(),
+    method: "new_default_meta",
+    args: {},
+  });
+  await root.call(
+    nft,
+    "nft_mint",
+    {
+      r1: {
+        n: 9,
+        d: 19,
+        b: 31,
+      },
+      r2: {
+        n: 6,
+        d: 18,
+        b: 3,
+      },
+      thickness: 0.5,
+      speed: 6,
+      receiver_id: root.accountId,
+    },
+    { attachedDeposit: "80000000000000000000000" }
+  );
+
+  const alice = await root.createSubAccount("alice", {
+    initialBalance: NEAR.parse("100 N").toJSON(),
+  });
+
+  const tokenReceiver = await root.devDeploy("../../res/token_receiver.wasm", {
+    initialBalance: NEAR.parse("100 N").toJSON(),
+    method: "new",
+    args: { non_fungible_token_account_id: nft },
+  });
+
+  const approvalReceiver = await root.devDeploy(
+    "../../res/approval_receiver.wasm",
+    {
+      initialBalance: NEAR.parse("100 N").toJSON(),
+      method: "new",
+      args: { non_fungible_token_account_id: nft },
+    }
+  );
+
+  t.context.worker = worker;
+  t.context.accounts = { root, alice, nft, tokenReceiver, approvalReceiver };
+});
+
+test.afterEach(async (t) => {
+  await t.context.worker.tearDown().catch((error) => {
+    console.log("Failed to tear down the worker:", error);
+  });
+});
+
+test("Final treasury balance after buy", async (test) => {
+  const { root, alice, nft, tokenReceiver } = test.context.accounts;
+  const root_bal = (await root.balance()).available;
[…]

### 2022-09-18 integration-tests/ts/src/utils.ts

@@ -1,0 +1,45 @@
+import { NearAccount, BN, tGas } from "near-workspaces";
+
+export async function helper_mint(
+  token_id: string,
+  root: NearAccount,
+  nft: NearAccount,
+  title: String,
+  desc: String
+) {
+  await root.call(
+    nft,
+    "nft_mint",
+    {
+      r1: {
+        n: parseInt(token_id),
+        d: 69,
+        b: 31,
+      },
+      r2: {
+        n: 6,
+        d: 18,
+        b: 31,
+      },
+      thickness: 0.5,
+      speed: 6,
+      receiver_id: root.accountId,
+    },
+    {
+      attachedDeposit: new BN("200700000000000000000000"), // need more deposit than the sim-tests, cause names are longer
+      gas: tGas("150"),
+    }
+  );
+}
+export async function mint_more(root: NearAccount, nft: NearAccount) {
+  await helper_mint("1", root, nft, "Black as the Night", "In charcoal");
+  await helper_mint("2", root, nft, "Hamakua", "Vintage recording");
+  await helper_mint("3", root, nft, "Aloha ke akua", "Original with piano");
+}
+
+export async function nft_total_supply(
+  nft: NearAccount,
+  user: NearAccount
+): Promise<BN> {
+  return new BN(await nft.view("nft_total_supply"));
+}

### 2022-09-18 frontend/src/config.ts
clean up the repo and add tests

@@ -1,4 +1,4 @@
-export const CONTRACT_NAME = process.env.CONTRACT_NAME || 'dev-1662738119804-26786917739875';
+export const CONTRACT_NAME = process.env.CONTRACT_NAME || 'dev-1663185605339-41690456082415';
 
 export function getConfig(env) {
   switch(env) {

### 2022-09-18 integration-tests/rs/src/tests.rs

@@ -1,0 +1,727 @@
+use near_units::{parse_gas, parse_near};
+use serde_json::json;
+use workspaces::prelude::*;
+use workspaces::{network::Sandbox, Account, Contract, Worker};
+
+const NFT_WASM_FILEPATH: &str = "../../res/non_fungible_token.wasm";
+const TR_WASM_FILEPATH: &str = "../../res/token_receiver.wasm";
+const AR_WASM_FILEPATH: &str = "../../res/approval_receiver.wasm";
+
+#[tokio::main]
+async fn main() -> anyhow::Result<()> {
+    // initiate environemnt
+    let worker = workspaces::sandbox().await?;
+
+    // deploy contracts
+    let nft_wasm = std::fs::read(NFT_WASM_FILEPATH)?;
+    let nft_contract = worker.dev_deploy(&nft_wasm).await?;
+    let tr_wasm = std::fs::read(TR_WASM_FILEPATH)?;
+    let tr_contract = worker.dev_deploy(&tr_wasm).await?;
+    let ar_wasm = std::fs::read(AR_WASM_FILEPATH)?;
+    let ar_contract = worker.dev_deploy(&ar_wasm).await?;
+
+    // create accounts
+    let owner = worker.root_account().unwrap();
+    let alice = owner
+        .create_subaccount(&worker, "alice")
+        .initial_balance(parse_near!("30 N"))
+        .transact()
+        .await?
+        .into_result()?;
+
+    // Initialize contracts
+    nft_contract
+        .call(&worker, "new_default_meta")
+        .args_json(serde_json::json!({}))?
+        .transact()
+        .await?;
+    tr_contract
+        .call(&worker, "new")
+        .args_json(serde_json::json!({
+            "non_fungible_token_account_id": nft_contract.id()
+        }))?
+        .transact()
+        .await?;
+    ar_contract
+        .call(&worker, "new")
+        .args_json(serde_json::json!({
+            "non_fungible_token_account_id": nft_contract.id()
+        }))?
+        .transact()
+        .await?;
+
+    // begin tests
+    test_simple_approve(&owner, &alice, &nft_contract, &worker).await?;
+    test_approval_simple_call(&owner, &nft_contract, &ar_contract, &worker).await?;
+    test_approved_account_transfers_token(&owner, &alice, &nft_contract, &worker).await?;
+    test_revoke(&owner, &alice, &nft_contract, &tr_contract, &worker).await?;
[…]

### 2022-09-18 nft/src/lib.rs

@@ -15,29 +15,32 @@ NOTES:
   - To prevent the deployed contract from being modified or deleted, it should not have any access
     keys on its account.
 */
+use near_sdk::collections::LookupMap;
 use std::convert::TryFrom;
 use std::str::Bytes;
 
 use near_contract_standards::non_fungible_token::metadata::{
     NFTContractMetadata, NonFungibleTokenMetadataProvider, TokenMetadata, NFT_METADATA_SPEC,
 };
-// use near_sdk::json_types::U128;
 use near_contract_standards::non_fungible_token::NonFungibleToken;
 use near_contract_standards::non_fungible_token::{Token, TokenId};
 use near_sdk::borsh::{self, BorshDeserialize, BorshSerialize};
 use near_sdk::collections::{LazyOption, LookupSet, UnorderedSet};
 use near_sdk::env::promise_batch_action_add_key_with_full_access;
-use near_sdk::json_types::ValidAccountId;
+use near_sdk::json_types::U128;
 use near_sdk::serde::{Deserialize, Serialize};
+use near_sdk::serde_json::json;
 use near_sdk::{
-    env, log, near_bindgen, AccountId, Balance, BorshStorageKey, PanicOnDefault, Promise,
-    PromiseOrValue,
+    assert_one_yocto, env, log, near_bindgen, AccountId, Balance, BorshStorageKey, PanicOnDefault,
+    Promise, PromiseOrValue,
 };
 
-near_sdk::setup_alloc!();
 
 pub const DEFAULT_MINT_PRICE: u128 = 10_u128;
 pub const DEFAULT_MAX_SUPPLY: u32 = 10;
+
+/// This is the name of the NFT standard we're using
+pub const NFT_STANDARD_NAME: &str = "nep171";
 
 #[derive(Serialize, Deserialize, BorshDeserialize, BorshSerialize, PanicOnDefault, Clone)]
 #[serde(crate = "near_sdk::serde")]
@@ -76,17 +79,21 @@ const DATA_IMAGE_SVG_NEAR_ICON: &str = "data:image/svg+xml,%3Csvg xmlns='http://
 impl Contract {
     #[init]
     pub fn new_default_meta() -> Self {
+        let zero_hash: Vec<u8> = vec![
+            0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,
+            0, 0, 0,
+        ];
         Self::new(
[…]

### 2022-09-18 scripts/build.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
 set -e
-cd "`dirname $0`"
-source flags.sh
+cd "`dirname $0`"/..
+source scripts/flags.sh
 cargo build --all --target wasm32-unknown-unknown --release
 cp target/wasm32-unknown-unknown/release/*.wasm ./res/

### 2022-09-18 tests/sim/main.rs

@@ -1,5 +1,0 @@
-mod test_approval;
-mod test_core;
-mod test_enumeration;
-mod test_3D_turtle;
-mod utils;

### 2022-09-18 tests/sim/test_3D_turtle.rs

@@ -1,250 +1,0 @@
-use std::convert::TryFrom;
-
-use crate::utils::{helper_mint, init};
-use near_contract_standards::non_fungible_token::Token;
-use near_sdk::{
-    env,
-    json_types::{ValidAccountId, U128},
-};
-use near_sdk_sim::{
-    call,
-    transaction::{ExecutionOutcome, ExecutionStatus},
-    view, ContractAccount, UserAccount,
-};
-use non_fungible_token::{
-    ContractContract as NftContract, Rational, DEFAULT_MAX_SUPPLY, DEFAULT_MINT_PRICE,
-};
-
-#[test]
-fn simulate_test_final_balance() {
-    let (root, nft, alice, _, _) = init();
-
-    let r1 = Rational { n: 1, d: 2, b: 3 };
-    let r2 = Rational { n: 2, d: 3, b: 4 };
-    let init_storage_usage: u64 = view!(nft.get_storage_usage()).unwrap_json();
-    let bal_init = alice.account().unwrap().amount;
-    let root_bal_init = root.account().unwrap().amount;
-
-    let call_ret = call!(
-        alice,
-        nft.nft_mint(r1.clone(), r2.clone(), 0.5f32, 2, alice.valid_account_id()),
-        70000000000000000000000, // deposit
-        300000000000000          // gas
-    );
-    let _: Vec<()> = call_ret
-        .promise_results()
-        .iter()
-        .map(|p| {
-            let p_r = p.as_ref().unwrap();
-            p_r.assert_success();
-            ()
-        })
-        .collect();
-
-    let final_storage_usage: u64 = view!(nft.get_storage_usage()).unwrap_json();
-    let storage_cost =
-        (final_storage_usage - init_storage_usage) as u128 * env::storage_byte_cost();
-    let bal_final = alice.account().unwrap().amount;
-
-    // TODO: why is this happening!!!!
-    // assert!(
-    //     bal_init - bal_final - (8547596185626000000010 - 7520000000000000000010)
-    //         <= storage_cost + DEFAULT_MINT_PRICE
-    //         && bal_init - bal_final >= storage_cost + DEFAULT_MINT_PRICE
-    // );
-    let root_bal_final = root.account().unwrap().amount;
-    assert!(root_bal_final - root_bal_init >= DEFAULT_MINT_PRICE);
-}
-
-#[test]
-fn simulate_test_burn() {
-    // Mints 1 token automatically
[…]

### 2022-09-18 tests/sim/test_enumeration.rs

@@ -1,125 +1,0 @@
-use crate::utils::{helper_mint, init};
-use near_contract_standards::non_fungible_token::Token;
-use near_sdk::json_types::U128;
-use near_sdk_sim::{view, ContractAccount, UserAccount};
-use non_fungible_token::{ContractContract as NftContract, Rational};
-
-fn mint_more(root: &UserAccount, nft: &ContractAccount<NftContract>) {
-    helper_mint(
-        Rational { n: 1, d: 2, b: 3 },
-        Rational { n: 2, d: 3, b: 4 },
-        root,
-        nft,
-        0.5f32,
-        1,
-    );
-    helper_mint(
-        Rational { n: 1, d: 2, b: 3 },
-        Rational { n: 2, d: 7, b: 4 },
-        root,
-        nft,
-        0.5f32,
-        1,
-    );
-    helper_mint(
-        Rational { n: 1, d: 2, b: 3 },
-        Rational { n: 2, d: 9, b: 4 },
-        root,
-        nft,
-        0.5f32,
-        1,
-    );
-}
-
-#[test]
-fn simulate_enum_total_supply() {
-    let (root, nft, _, _, _) = init();
-    mint_more(&root, &nft);
-
-    let total_supply: U128 = view!(nft.nft_total_supply()).unwrap_json();
-    assert_eq!(total_supply, U128::from(4));
-}
-
-#[test]
-fn simulate_enum_nft_tokens() {
-    let (root, nft, _, _, _) = init();
-    mint_more(&root, &nft);
-
-    // No optional args should return all
-    let mut tokens: Vec<Token> = view!(nft.nft_tokens(None, None)).unwrap_json();
-    assert_eq!(tokens.len(), 4);
-    // Start at "1", with no limit arg
-    tokens = view!(nft.nft_tokens(Some(U128::from(1)), None)).unwrap_json();
-    assert_eq!(tokens.len(), 3);
-    assert_eq!(tokens.get(0).unwrap().token_id, "1".to_string());
-    assert_eq!(tokens.get(1).unwrap().token_id, "2".to_string());
-    assert_eq!(tokens.get(2).unwrap().token_id, "3".to_string());
-
-    // Start at "2", with limit 1
-    tokens = view!(nft.nft_tokens(Some(U128::from(2)), Some(1u64))).unwrap_json();
-    assert_eq!(tokens.len(), 1);
-    assert_eq!(tokens.get(0).unwrap().token_id, "2".to_string());
-
[…]

### 2022-09-18 tests/sim/utils.rs

@@ -1,107 +1,0 @@
-use approval_receiver::ApprovalReceiverContract;
-use non_fungible_token::ContractContract as NftContract;
-use non_fungible_token::Rational;
-use token_receiver::TokenReceiverContract;
-
-use near_sdk_sim::{call, deploy, init_simulator, to_yocto, ContractAccount, UserAccount};
-
-// Load in contract bytes at runtime
-near_sdk_sim::lazy_static_include::lazy_static_include_bytes! {
-    NFT_WASM_BYTES => "res/non_fungible_token.wasm",
-    TOKEN_RECEIVER_WASM_BYTES => "res/token_receiver.wasm",
-    APPROVAL_RECEIVER_WASM_BYTES => "res/approval_receiver.wasm",
-}
-
-const NFT_ID: &str = "nft";
-const TOKEN_RECEIVER_ID: &str = "token-receiver";
-const APPROVAL_RECEIVER_ID: &str = "approval-receiver";
-
-// TODO: how to export String instead of &str? Way too much `into`/`to_string` with &str.
-pub const TOKEN_ID: &str = "0";
-
-/// Initialize simulator and return:
-/// * root: the root user, set as owner_id for NFT contract, owns a token with ID=1
-/// * nft: the NFT contract, callable with `call!` and `view!`
-/// * alice: a user account, does not yet own any tokens
-/// * token_receiver: a contract implementing `nft_on_transfer` for use with `transfer_and_call`
-pub fn init() -> (
-    UserAccount,
-    ContractAccount<NftContract>,
-    UserAccount,
-    ContractAccount<TokenReceiverContract>,
-    ContractAccount<ApprovalReceiverContract>,
-) {
-    let root = init_simulator(None);
-    // uses default values for deposit and gas
-    let nft = deploy!(
-        // Contract Proxy
-        contract: NftContract,
-        // Contract account id
-        contract_id: NFT_ID,
-        // Bytes of contract
-        bytes: &NFT_WASM_BYTES,
-        // User deploying the contract,
-        signer_account: root,
-        // init method
-        init_method: new_default_meta()
-    );
-
-    call!(
-        root,
-        nft.nft_mint(
-            Rational {
-                n: 10,
-                d: 11,
-                b: 14,
-            },
-            Rational {
-                n: 10,
-                d: 11,
-                b: 13,
-            },
-            0.5f32,
-            10,
-            root.valid_account_id()
[…]

### 2022-09-18 nft/src/lib.rs
compliments

@@ -24,7 +24,7 @@ use near_contract_standards::non_fungible_token::metadata::{
 };
 use near_contract_standards::non_fungible_token::NonFungibleToken;
 use near_contract_standards::non_fungible_token::{Token, TokenId};
-use near_sdk::borsh::{self, BorshDeserialize, BorshSerialize};
+use near_sdk::borsh::{self, de, BorshDeserialize, BorshSerialize};
 use near_sdk::collections::{LazyOption, LookupSet, UnorderedSet};
 use near_sdk::env::promise_batch_action_add_key_with_full_access;
 use near_sdk::json_types::U128;
@@ -34,7 +34,6 @@ use near_sdk::{
     assert_one_yocto, env, log, near_bindgen, AccountId, Balance, BorshStorageKey, PanicOnDefault,
     Promise, PromiseOrValue,
 };
-
 
 pub const DEFAULT_MINT_PRICE: u128 = 10_u128;
 pub const DEFAULT_MAX_SUPPLY: u32 = 10;
@@ -141,12 +140,33 @@ impl Contract {
         let r1_simplified = r1.reduce();
         let r2_simplified = r2.reduce();
 
+        let r1_compliment = r1_simplified.complement();
+        let r2_compliment = r2_simplified.complement();
+
         if self
             .minted_rational_pairs
             .contains(&(r1_simplified.clone(), r2_simplified.clone()))
             || self
                 .minted_rational_pairs
                 .contains(&(r2_simplified.clone(), r1_simplified.clone()))
+            || self
+                .minted_rational_pairs
+                .contains(&(r1_compliment.clone(), r2_compliment.clone()))
+            || self
+                .minted_rational_pairs
+                .contains(&(r2_compliment.clone(), r1_compliment.clone()))
+            || self
+                .minted_rational_pairs
+                .contains(&(r1_compliment.clone(), r2_simplified.clone()))
+            || self
+                .minted_rational_pairs
+                .contains(&(r1_simplified.clone(), r2_compliment.clone()))
+            || self
+                .minted_rational_pairs
+                .contains(&(r2_simplified.clone(), r1_compliment.clone()))
+            || self
+                .minted_rational_pairs
+                .contains(&(r2_simplified.clone(), r1_compliment.clone()))
         {
             return true;
         }
@@ -344,24 +364,62 @@ impl Contract {
 
 /// From Stack Overflow: https://codereview.stackexchange.com/questions/165283/fraction-type-in-rust
[…]

### 2022-09-18 frontend/src/config.ts
change frontend endpoint

@@ -1,4 +1,4 @@
-export const CONTRACT_NAME = process.env.CONTRACT_NAME || 'dev-1663185605339-41690456082415';
+export const CONTRACT_NAME = process.env.CONTRACT_NAME || 'dev-1663542361700-89481516959712'
 
 export function getConfig(env) {
   switch(env) {

### 2022-09-18 nft/src/lib.rs

@@ -41,7 +41,16 @@ pub const DEFAULT_MAX_SUPPLY: u32 = 10;
 /// This is the name of the NFT standard we're using
 pub const NFT_STANDARD_NAME: &str = "nep171";
 
-#[derive(Serialize, Deserialize, BorshDeserialize, BorshSerialize, PanicOnDefault, Clone)]
+#[derive(
+    Debug,
+    PartialEq,
+    Serialize,
+    Deserialize,
+    BorshDeserialize,
+    BorshSerialize,
+    PanicOnDefault,
+    Clone,
+)]
 #[serde(crate = "near_sdk::serde")]
 pub struct Rational {
     /// numerator
@@ -140,8 +149,8 @@ impl Contract {
         let r1_simplified = r1.reduce();
         let r2_simplified = r2.reduce();
 
-        let r1_compliment = r1_simplified.complement();
-        let r2_compliment = r2_simplified.complement();
+        let r1_compliment = r1_simplified.compliment();
+        let r2_compliment = r2_simplified.compliment();
 
         if self
             .minted_rational_pairs
@@ -149,27 +158,49 @@ impl Contract {
             || self
                 .minted_rational_pairs
                 .contains(&(r2_simplified.clone(), r1_simplified.clone()))
-            || self
-                .minted_rational_pairs
-                .contains(&(r1_compliment.clone(), r2_compliment.clone()))
-            || self
-                .minted_rational_pairs
-                .contains(&(r2_compliment.clone(), r1_compliment.clone()))
-            || self
-                .minted_rational_pairs
-                .contains(&(r1_compliment.clone(), r2_simplified.clone()))
-            || self
-                .minted_rational_pairs
-                .contains(&(r1_simplified.clone(), r2_compliment.clone()))
-            || self
-                .minted_rational_pairs
-                .contains(&(r2_simplified.clone(), r1_compliment.clone()))
-            || self
-                .minted_rational_pairs
-                .contains(&(r2_simplified.clone(), r1_compliment.clone()))
         {
             return true;
         }
+        if let Some(r1_compliment) = r1_compliment.clone() {
+            if self
+                .minted_rational_pairs
+                .contains(&(r1_compliment.clone(), r2_simplified.clone()))
+                || self
+                    .minted_rational_pairs
+                    .contains(&(r2_simplified.clone(), r1_compliment.clone()))
+            {
+                return true;
+            }
+        }
+        if let Some(r2_compliment) = r2_compliment.clone() {
+            if self
[…]

### 2022-09-19 frontend/src/config.ts
fix contract and test

@@ -1,59 +1,62 @@
-export const CONTRACT_NAME = process.env.CONTRACT_NAME || 'dev-1663542361700-89481516959712'
+export const CONTRACT_NAME =
+  process.env.CONTRACT_NAME || "dev-1663542361700-89481516959712";
 
 export function getConfig(env) {
-  switch(env) {
-    case 'mainnet':
+  switch (env) {
+    case "mainnet":
       return {
-        networkId: 'mainnet',
-        nodeUrl: 'https://rpc.mainnet.near.org',
+        networkId: "mainnet",
+        nodeUrl: "https://rpc.mainnet.near.org",
         contractName: CONTRACT_NAME,
-        walletUrl: 'https://wallet.near.org',
-        helperUrl: 'https://helper.mainnet.near.org'
+        walletUrl: "https://wallet.near.org",
+        helperUrl: "https://helper.mainnet.near.org",
       };
     // This is an example app so production is set to testnet.
     // You can move production to mainnet if that is applicable.
-    case 'production':
-    case 'development':
-    case 'testnet':
+    case "production":
+    case "development":
+    case "testnet":
       return {
-        networkId: 'testnet',
-        nodeUrl: 'https://rpc.testnet.near.org',
+        networkId: "testnet",
+        nodeUrl: "https://rpc.testnet.near.org",
         contractName: CONTRACT_NAME,
-        walletUrl: 'https://wallet.testnet.near.org',
-        helperUrl: 'https://helper.testnet.near.org'
+        walletUrl: "https://wallet.testnet.near.org",
+        helperUrl: "https://helper.testnet.near.org",
       };
-    case 'betanet':
+    case "betanet":
       return {
-        networkId: 'betanet',
-        nodeUrl: 'https://rpc.betanet.near.org',
+        networkId: "betanet",
+        nodeUrl: "https://rpc.betanet.near.org",
         contractName: CONTRACT_NAME,
-        walletUrl: 'https://wallet.betanet.near.org',
-        helperUrl: 'https://helper.betanet.near.org'
+        walletUrl: "https://wallet.betanet.near.org",
+        helperUrl: "https://helper.betanet.near.org",
       };
-    case 'local':
+    case "local":
       return {
-        networkId: 'local',
-        nodeUrl: 'http://localhost:3030',
+        networkId: "local",
+        nodeUrl: "http://localhost:3030",
         keyPath: `${process.env.HOME}/.near/validator_key.json`,
[…]

### 2022-09-19 integration-tests/ts/src/main.ava.ts

@@ -24,6 +24,7 @@ test.beforeEach(async (t) => {
     method: "new_default_meta",
     args: {},
   });
+
   await root.call(
     nft,
     "nft_mint",
@@ -108,7 +109,7 @@ test("Final treasury balance after buy", async (test) => {
 test("Mint maximum number of tokens and then burn to mint one more. Then exceed max supply", async (test) => {
   const { root, alice, nft, tokenReceiver } = test.context.accounts;
   //   Subtract 1 to account for the mint in initialization
-  for (let i = 0; i < DEFAULT_MAX_SUPPLY - 1; i++) {
+  for (let i = 1; i < DEFAULT_MAX_SUPPLY - 1; i++) {
     await alice.call(
       nft,
       "nft_mint",

### 2022-09-19 nft/src/lib.rs

@@ -145,7 +145,7 @@ impl Contract {
     }
 
     // TODO: factor out dup code
-    pub fn nft_minted(&self, r1: Rational, r2: Rational) -> bool {
+    pub fn nft_minted(&self, r1: &Rational, r2: &Rational) -> bool {
         let r1_simplified = r1.reduce();
         let r2_simplified = r2.reduce();
 
@@ -310,12 +310,11 @@ impl Contract {
             panic!("Cannot mint more than {} tokens", self.max_supply);
         }
 
-        let r1_simplified = r1.reduce();
-        let r2_simplified = r2.reduce();
-
-        if self.nft_minted(r1_simplified.clone(), r2_simplified.clone()) {
+        if self.nft_minted(&r1, &r2) {
             panic!("These fractions have already been minted!");
         }
+        let r1_simplified = r1.reduce();
+        let r2_simplified = r2.reduce();
 
         self.minted_rational_pairs
             .insert(&(r1_simplified.clone(), r2_simplified.clone()));
@@ -394,7 +393,10 @@ impl Rational {
     /// Here we assume that the rational is reduced (i.e. below 1) and the gcd of numerator and denominator is 1
     pub fn compliment(&self) -> Option<Self> {
         if self.n == 0 || self.d == 0 || self.b == 0 {
-            panic!("Cannot have 0 numerator, denominator, or base");
+            panic!(
+                "Cannot have 0 numerator, denominator, or base. Current is n: {}, d: {}, b: {}",
+                self.n, self.d, self.b
+            );
         }
         if self.b == 1 {
             panic!("Cannot have a base of 1");
@@ -429,18 +431,18 @@ impl Rational {
         }
         let moded_n = self.n % self.d;
         let gcd_num_denom = gcd(moded_n, self.d);
-        let moded_n = moded_n / gcd_num_denom;
-        let moded_d = self.d / gcd_num_denom;
+        let moded_n_red = moded_n / gcd_num_denom;
+        let moded_d_red = self.d / gcd_num_denom;
 
-        let num_reduced_by_mul_base = if moded_n % self.b == 0 {
-            moded_n / self.b
+        let num_reduced_by_mul_base = if moded_n_red % self.b == 0 {
+            moded_n_red / self.b
         } else {
-            moded_n
+            moded_n_red
         };
[…]

### 2022-09-19 integration-tests/ts/src/main.ava.ts
update tests

@@ -109,7 +109,8 @@ test("Final treasury balance after buy", async (test) => {
 test("Mint maximum number of tokens and then burn to mint one more. Then exceed max supply", async (test) => {
   const { root, alice, nft, tokenReceiver } = test.context.accounts;
   //   Subtract 1 to account for the mint in initialization
-  for (let i = 1; i < DEFAULT_MAX_SUPPLY - 1; i++) {
+  for (let i = 1; i < DEFAULT_MAX_SUPPLY; i++) {
+    console.log("GOING TO ", i);
     await alice.call(
       nft,
       "nft_mint",
@@ -117,7 +118,7 @@ test("Mint maximum number of tokens and then burn to mint one more. Then exceed 
         r1: {
           n: i * 17,
           d: 1999,
-          b: 3,
+          b: 87,
         },
         r2: {
           n: 6,
@@ -167,7 +168,7 @@ test("Mint maximum number of tokens and then burn to mint one more. Then exceed 
         r1: {
           n: 19 * 17,
           d: 1999,
-          b: 3,
+          b: 87,
         },
         r2: {
           n: 6,

### 2022-09-19 nft/src/lib.rs

@@ -574,6 +574,22 @@ mod tests {
 
         let r = Rational { n: 1, d: 1, b: 3 };
         assert_eq!(r.compliment(), None);
+
+        let r = Rational {
+            n: 3 * 17,
+            d: 1999,
+            b: 3,
+        }
+        .reduce();
+        assert_eq!(
+            r,
+            Rational {
+                n: 17,
+                d: 1999,
+                b: 3
+            }
+        );
+        assert_eq!(r.compliment().unwrap(), Rational { n: 655, d: 3998, b: 3 });
     }
 
     #[test]
@@ -591,7 +607,7 @@ mod tests {
         assert_eq!(
             Rational { n: 9, d: 19, b: 31 }.reduce(),
             Rational { n: 9, d: 19, b: 31 }
-        )
+        );
     }
 
     // #[test]

### 2022-09-19 frontend/src/config.ts
deploy scripts and testnet final contract

@@ -1,5 +1,5 @@
 export const CONTRACT_NAME =
-  process.env.CONTRACT_NAME || "dev-1663542361700-89481516959712";
+  process.env.CONTRACT_NAME || "three_d_turtle.groked.testnet";
 
 export function getConfig(env) {
   switch (env) {

### 2022-09-19 integration-tests/ts/src/main.ava.ts

@@ -110,7 +110,6 @@ test("Mint maximum number of tokens and then burn to mint one more. Then exceed 
   const { root, alice, nft, tokenReceiver } = test.context.accounts;
   //   Subtract 1 to account for the mint in initialization
   for (let i = 1; i < DEFAULT_MAX_SUPPLY; i++) {
-    console.log("GOING TO ", i);
     await alice.call(
       nft,
       "nft_mint",
@@ -311,7 +310,6 @@ test("Underpaying attached deposit", async (test) => {
     test.assert(true, "Under depositing tokens failed as expected");
   }
 });
-
 
 /*
 

### 2022-09-19 nft/src/lib.rs

@@ -110,6 +110,37 @@ impl Contract {
     }
 
     #[init]
+    #[payable]
+    pub fn new_default_only_meta(
+        owner_id: AccountId,
+        treasury_id: AccountId,
+        mint_price: U128,
+        max_supply: u32,
+        base_url: String,
+    ) -> Self {
+        let zero_hash: Vec<u8> = vec![
+            0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,
+            0, 0, 0,
+        ];
+        Self::new(
+            owner_id,
+            treasury_id,
+            NFTContractMetadata {
+                spec: NFT_METADATA_SPEC.to_string(),
+                name: "3D Turtles".to_string(),
+                symbol: "3DTURT".to_string(),
+                icon: Some(DATA_IMAGE_SVG_NEAR_ICON.to_string()), // TODO:
+                base_uri: None,
+                reference: Some("https://github.com/Lev-Stambler/3D-Turtles".to_string()),
+                reference_hash: Some(zero_hash.into()),
+            },
+            mint_price,
+            max_supply,
+            base_url,
+        )
+    }
+
+    #[init]
     pub fn new(
         owner_id: AccountId,
         treasury_id: AccountId,
@@ -589,7 +620,14 @@ mod tests {
                 b: 3
             }
         );
-        assert_eq!(r.compliment().unwrap(), Rational { n: 655, d: 3998, b: 3 });
+        assert_eq!(
+            r.compliment().unwrap(),
+            Rational {
+                n: 655,
+                d: 3998,
+                b: 3
+            }
+        );
     }
 
     #[test]

### 2022-09-19 scripts/mainnet-deploy.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+# Run from root of folder
+./scripts/build.sh
+
+./scripts/build.sh && \
+	near dev-deploy ./res/non_fungible_token.wasm --accountId 'levtester.testnet' && \
+	source neardev/dev-account.env && \
+	echo "Deployed to $CONTRACT_NAME" && \
+	near call $CONTRACT_NAME new_default_meta "" --accountId 'levtester.testnet'

### 2022-09-19 scripts/testnet-contract-create.sh

@@ -1,0 +1,5 @@
+#!/bin/sh
+CONTRACT_ACCOUNT_ID='three_d_turtle.groked.testnet'
+DEP_ACCOUNT='groked.testnet'
+
+near create-account "$CONTRACT_ACCOUNT_ID" --masterAccount "$DEP_ACCOUNT"

### 2022-09-19 scripts/testnet-deploy.sh

@@ -1,0 +1,22 @@
+#!/bin/bash
+CONTRACT_ACCOUNT_ID='three_d_turtle.groked.testnet'
+DEP_ACCOUNT='groked.testnet'
+TREASURY_ID='groked.testnet'
+# 6 Near
+MINT_PRICE=6000000000000000000000000
+BASE_URL='https://3d-turtle.netlify.app/#'
+# 150 TGas
+INIT_GAS=150000000000000
+# 0.5 Near
+INIT_DEP=0.5
+
+# 100,000 for testnet
+MAX_SUPPLY=100000
+
+INIT_ARGS="{\"owner_id\": \"$CONTRACT_ACCOUNT_ID\", \"treasury_id\": \"$TREASURY_ID\", \"mint_price\": \"$MINT_PRICE\", \"max_supply\": $MAX_SUPPLY, \"base_url\": \"$BASE_URL\"}"
+
+echo "Init args of $INIT_ARGS"
+
+# Run from root of folder
+./scripts/build.sh && \
+near deploy $CONTRACT_ACCOUNT_ID ./res/non_fungible_token.wasm new_default_only_meta "$INIT_ARGS" "$INIT_GAS" "$INIT_DEP"

### 2022-09-25 paper/Paper.tex
change frontend endpoint
mainnet deploy

@@
   \centering
-  \includegraphics[width=8cm]{fig/turtle.png}
-  \caption{The above is a placeholder, I would like to get Shiva to help me design a 3D graphic here similar to Figure 1 but in 3D}
+  \includegraphics[width=8cm]{fig/turtle3dtimestep.png}
+  \caption{An example of a turtle updating its rotational direction.}
 \end{figure}
@@
 to close. In other words, the turtle would go off in one direction forever.
-% TODO: picture of failing to close in 3d space
 But, the turtle \textit{sometimes} closed.
@@
   \includegraphics[width=8cm]{fig/failclose3d.png}
-  \caption{A non closing 3D shape generated from $\frac{102}{999} = 0.\overline{102}$ and $\frac{223}{999} = 0.\overline{223}$ in base 10.}
+  \caption{A non closing 3D shape generated from $\frac{7}{11} = 0.\overline{63}$ and $\frac{10}{11} = 0.\overline{90}$ in base 10.}
 \end{figure}
@@
   \includegraphics[width=8cm]{fig/tempclose.jpeg}
-  \caption{A closing 3D shape generate from (?????... this is a placeholder).}
+  \caption{A closing 3D shape generate from $\frac{7}{13}$ and $\frac{2}{3}$ in base $10$.}
 \end{figure}
@@
 \pagebreak
+\section{Finding Duplicates}
+- TODO: proof of comp
+- difficulty of otherwise
+
 \section{Open Questions and Future Work}

### 2022-09-25 frontend/src/config.ts

@@ -1,5 +1,5 @@
 export const CONTRACT_NAME =
-  process.env.CONTRACT_NAME || "three_d_turtle.groked.testnet";
+  process.env.CONTRACT_NAME || "three_d_turtle.neontetra.near";
 
 export function getConfig(env) {
   switch (env) {

### 2022-09-25 frontend/src/math/rationals.ts

@@ -1,70 +1,74 @@
-import { MAX_PREVIEW_STEPS, type Rational } from '../interfaces';
+import { MAX_PREVIEW_STEPS, type Rational } from "../interfaces";
 
 /**
  * Get the rotation amount for the next angle.
  * It accumulates the angle amount
  */
-export function* getRationalAngleIterator(rational: Rational): IterableIterator<number> {
-	let curr = 0;
-	let remainder = rational.n;
-	for (;;) {
-		let digit = Math.floor((remainder * rational.b) / rational.d);
-		remainder = (remainder * rational.b) % rational.d;
-		curr += digit;
-		yield curr;
-	}
+export function* getRationalAngleIterator(
+  rational: Rational
+): IterableIterator<number> {
+  let curr = 0;
+  let remainder = rational.n;
+  for (;;) {
+    let digit = Math.floor((remainder * rational.b) / rational.d);
+    remainder = (remainder * rational.b) % rational.d;
+    curr += digit;
+    yield curr;
+  }
 }
 
 // baked version of getRationalAngleIterator
 // runs for MAX_PREVIEW_STEPS
 export function precomputeRationalAngles(rational: Rational): number[] {
-	let angles: number[] = [];
-	let curr = 0;
-	let remainder = rational.n;
-	for (let i = 0; i < MAX_PREVIEW_STEPS; i++) {
-		let digit = Math.floor((remainder * rational.b) / rational.d);
-		remainder = (remainder * rational.b) % rational.d;
-		curr += digit;
-		angles = [...angles, curr];
-	}
+  let angles: number[] = [];
+  let curr = 0;
+  let remainder = rational.n;
+  for (let i = 0; i < MAX_PREVIEW_STEPS; i++) {
+    let digit = Math.floor((remainder * rational.b) / rational.d);
+    remainder = (remainder * rational.b) % rational.d;
+    curr += digit;
+    angles = [...angles, curr];
+  }
 
-	return angles;
+  return angles;
 }
 
 /**
  * Get the rotation amount for the next angle.
  * It accumulates the angle amount
  */
-export function* getRationalDistanceIterator(rational: Rational): IterableIterator<number> {
-	let remainder = rational.n;
-	for (;;) {
-		let digit = Math.floor((remainder * rational.b) / rational.d);
-		remainder = (remainder * rational.b) % rational.d;
-		yield digit;
-	}
[…]

### 2022-09-25 frontend/src/near.ts

@@ -10,7 +10,7 @@ const nearAPI = window.nearApi
 // create a keyStore for signing transactions using the user's key
 // which is located in the browser local storage after user logs in
 let keyStore;
-const env = "testnet";
+const env = "mainnet";
 
 let nearConfig;
 

### 2022-09-25 scripts/mainnet-contract-create.sh

@@ -1,0 +1,5 @@
+#!/bin/sh
+CONTRACT_ACCOUNT_ID='three_d_turtle.neontetra.near'
+DEP_ACCOUNT='neontetra.near'
+
+NEAR_ENV=mainnet near create-account "$CONTRACT_ACCOUNT_ID" --masterAccount "$DEP_ACCOUNT"

### 2022-09-25 scripts/mainnet-deploy.sh

@@ -1,9 +1,23 @@
 #!/bin/bash
-# Run from root of folder
-./scripts/build.sh
+CONTRACT_ACCOUNT_ID='three_d_turtle.neontetra.near'
+DEP_ACCOUNT='neontetra.near'
+TREASURY_ID='neontetra.near'
+# 6 Near
+MINT_PRICE=6000000000000000000000000
+BASE_URL='https://3dturtles.groked.co'
+# 150 TGas
+INIT_GAS=150000000000000
+# 0.5 Near
+INIT_DEP=0.5
 
+# 8,888 for mainnet
+MAX_SUPPLY=8888
+
+INIT_ARGS="{\"owner_id\": \"$CONTRACT_ACCOUNT_ID\", \"treasury_id\": \"$TREASURY_ID\", \"mint_price\": \"$MINT_PRICE\", \"max_supply\": $MAX_SUPPLY, \"base_url\": \"$BASE_URL\"}"
+
+echo "Init args of $INIT_ARGS"
+
+# Run from root of folder
 ./scripts/build.sh && \
-	near dev-deploy ./res/non_fungible_token.wasm --accountId 'levtester.testnet' && \
-	source neardev/dev-account.env && \
-	echo "Deployed to $CONTRACT_NAME" && \
-	near call $CONTRACT_NAME new_default_meta "" --accountId 'levtester.testnet'
+NEAR_ENV=mainnet near deploy $CONTRACT_ACCOUNT_ID ./res/non_fungible_token.wasm new_default_only_meta "$INIT_ARGS" "$INIT_GAS" "$INIT_DEP" --networkId "mainnet"
+

### 2022-09-25 scripts/testnet-deploy.sh

@@ -4,7 +4,7 @@ DEP_ACCOUNT='groked.testnet'
 TREASURY_ID='groked.testnet'
 # 6 Near
 MINT_PRICE=6000000000000000000000000
-BASE_URL='https://3d-turtle.netlify.app/#'
+BASE_URL='https://3d-turtle.netlify.app'
 # 150 TGas
 INIT_GAS=150000000000000
 # 0.5 Near

### 2022-09-25 frontend/src/near.ts
update mint amount

@@ -43,7 +43,7 @@ const getContract = (near: Near): Contract => {
   return contract;
 };
 
-const MINT_AMOUNT = 10;
+const MINT_AMOUNT = 6000000000000000000000000;
 
 export const mint = async (
   near: Near,

### 2022-09-28 frontend/src/near.ts
gallery

@@ -5,7 +5,16 @@ import { CONTRACT_NAME, getConfig } from "./config";
 import type { Rational } from "./interfaces";
 
 //@ts-ignore
-const nearAPI = window.nearApi
+const nearAPI = window.nearApi;
+
+export interface Token {
+  token_id: string;
+  owner_id: string;
+  metadata: {
+    media: string;
+    title: string
+  };
+}
 
 // create a keyStore for signing transactions using the user's key
 // which is located in the browser local storage after user logs in
@@ -17,7 +26,7 @@ let nearConfig;
 export const near: Writable<Near | null> = writable(null);
 
 export const setNear = async () => {
-  console.log(nearAPI, nearAPI.keyStores)
+  console.log(nearAPI, nearAPI.keyStores);
   keyStore = new nearAPI.keyStores.BrowserLocalStorageKeyStore();
   nearConfig = {
     keyStore,
@@ -37,7 +46,7 @@ const getContract = (near: Near): Contract => {
   const account = getWalletConnection(near).account();
   const contract = new nearAPI.Contract(account, CONTRACT_NAME, {
     // name of contract you're connecting to
-    viewMethods: ["nft_minted"], // view methods do not change state but usually return a value
+    viewMethods: ["nft_minted", "nft_tokens_for_owner", "nft_tokens"], // view methods do not change state but usually return a value
     changeMethods: ["nft_mint"], // change methods modify state
   });
   return contract;
@@ -66,6 +75,25 @@ export const mint = async (
       BigInt(MINT_AMOUNT) + BigInt(nearAPI.utils.format.parseNearAmount("0.1"))
     ).toString()
   );
+};
+
+export const tokensByAccount = async (near, account: string): Promise<Token[]> => {
+  //@ts-ignore
+  const contract = getContract(near);
+  //@ts-ignore
+  const tokens: Token[] = await contract.nft_tokens_for_owner({
+    account_id: account,
+  });
+  return tokens;
+};
+
+export const getAllTokens = async (near): Promise<Token[]> => {
+  //@ts-ignore
+  const contract = getContract(near);
+  //@ts-ignore
+  const tokens: Token[] = await contract.nft_tokens({
+  });
+  return tokens;
 };
 
 export const checkMinted = async (

### 2022-09-28 nft/src/lib.rs
frontend gallery

@@ -15,14 +15,17 @@ NOTES:
   - To prevent the deployed contract from being modified or deleted, it should not have any access
     keys on its account.
 */
+use near_contract_standards::non_fungible_token::core::StorageKey;
+use near_contract_standards::non_fungible_token::events::NftMint;
 use near_sdk::collections::LookupMap;
+use std::collections::HashMap;
 use std::convert::TryFrom;
 use std::str::Bytes;
 
 use near_contract_standards::non_fungible_token::metadata::{
     NFTContractMetadata, NonFungibleTokenMetadataProvider, TokenMetadata, NFT_METADATA_SPEC,
 };
-use near_contract_standards::non_fungible_token::NonFungibleToken;
+use near_contract_standards::non_fungible_token::{refund_deposit_to_account, NonFungibleToken};
 use near_contract_standards::non_fungible_token::{Token, TokenId};
 use near_sdk::borsh::{self, de, BorshDeserialize, BorshSerialize};
 use near_sdk::collections::{LazyOption, LookupSet, UnorderedSet};
@@ -226,12 +229,6 @@ impl Contract {
             }
         }
 
-        // self.   .minted_rational_pairs
-        //                 .contains(&(r1_compliment.clone(), r2_compliment.clone()))
-        //             || self
-        //                 .minted_rational_pairs
-        //                 .contains(&(r2_compliment.clone(), r1_compliment.clone()))
-
         return false;
     }
 
@@ -314,6 +311,91 @@ impl Contract {
         result
     }
 
+    // Copy and pasted from Near's library except modified storage refund to not refund mint cost
+    /// Mint a new token without checking:
+    /// * Whether the caller id is equal to the `owner_id`
+    /// * `refund_id` will transfer the left over balance after storage costs are calculated to the provided account.
+    ///   Typically the account will be the owner. If `None`, will not refund. This is useful for delaying refunding
+    ///   until multiple tokens have been minted.
+    ///
+    /// Returns the newly minted token and does not emit the mint event. This allows minting multiple before emitting.
+    fn internal_mint_no_with_refund(
+        &mut self,
+        token_id: TokenId,
+        token_owner_id: AccountId,
+        token_metadata: Option<TokenMetadata>,
+        refund_id: Option<AccountId>,
+        cost: u128,
+    ) -> Token {
+        // Remember current storage usage if refund_id is Some
+        let initial_storage_usage = refund_id.map(|account_id| (account_id, env::storage_usage()));
+
[…]

### 2022-09-28 scripts/mainnet-deploy.sh

@@ -19,5 +19,5 @@ echo "Init args of $INIT_ARGS"
 
 # Run from root of folder
 ./scripts/build.sh && \
-NEAR_ENV=mainnet near deploy $CONTRACT_ACCOUNT_ID ./res/non_fungible_token.wasm new_default_only_meta "$INIT_ARGS" "$INIT_GAS" "$INIT_DEP" --networkId "mainnet"
+NEAR_ENV=mainnet near deploy $CONTRACT_ACCOUNT_ID ./res/non_fungible_token.wasm new_default_only_meta "$INIT_ARGS" "$INIT_GAS" "$INIT_DEP" --networkId "mainnet" 
 

### 2022-09-28 frontend/src/near.ts
frontend gallery

@@ -3,6 +3,7 @@ import type { Contract, Near, utils } from "near-api-js";
 import { writable, type Writable } from "svelte/store";
 import { CONTRACT_NAME, getConfig } from "./config";
 import type { Rational } from "./interfaces";
+import { setCurrentRationals } from "./turtle_utils";
 
 //@ts-ignore
 const nearAPI = window.nearApi;
@@ -12,7 +13,7 @@ export interface Token {
   owner_id: string;
   metadata: {
     media: string;
-    title: string
+    title: string;
   };
 }
 
@@ -61,6 +62,7 @@ export const mint = async (
   thickness: number,
   speed: number
 ): Promise<void> => {
+  setCurrentRationals(r1, r2, { n: 8, d: 9, b: 10 });
   //@ts-ignore
   await getContract(near).nft_mint(
     {
@@ -77,7 +79,10 @@ export const mint = async (
   );
 };
 
-export const tokensByAccount = async (near, account: string): Promise<Token[]> => {
+export const tokensByAccount = async (
+  near,
+  account: string
+): Promise<Token[]> => {
   //@ts-ignore
   const contract = getContract(near);
   //@ts-ignore
@@ -91,8 +96,7 @@ export const getAllTokens = async (near): Promise<Token[]> => {
   //@ts-ignore
   const contract = getContract(near);
   //@ts-ignore
-  const tokens: Token[] = await contract.nft_tokens({
-  });
+  const tokens: Token[] = await contract.nft_tokens({});
   return tokens;
 };
 

### 2022-09-28 frontend/src/store.ts

@@ -1,133 +1,146 @@
-import { writable, type Writable } from 'svelte/store';
-import type { Angle, Rational } from './interfaces';
+import { writable, type Writable } from "svelte/store";
+import type { Angle, Rational } from "./interfaces";
 import {
-	getRationalAngleIterator,
-	getRationalDistanceIterator,
-	precomputeRationalAngles,
-	precomputeRationalDistances,
-	rationalFromStr
-} from './math/rationals';
+  getRationalAngleIterator,
+  getRationalDistanceIterator,
+  precomputeRationalAngles,
+  precomputeRationalDistances,
+  rationalFromStr,
+} from "./math/rationals";
+import { getCurrentRationals } from "./turtle_utils";
 
 export type StoredParameters = {
-	initParams: [Rational, Rational, Rational];
-	angles: Angle[];
-	distance: IterableIterator<number>;
-	distance_preview: number[];
+  initParams: [Rational, Rational, Rational];
+  angles: Angle[];
+  distance: IterableIterator<number>;
+  distance_preview: number[];
 };
 
 export const default_angle_1: Rational = { n: 7, d: 213, b: 4 };
 export const default_angle_2: Rational = { n: 21, d: 11, b: 9 };
 export const default_distance: Rational = { n: 8, d: 9, b: 10 };
 
-export const generateParams = (a1: Rational, a2: Rational, d: Rational): any => {
-	return {
-		initParams: [a1, a2, d],
-		angles: [
-			{
-				iterator: getRationalAngleIterator({
-					n: a1.n,
-					d: a1.d,
-					b: a1.b
-				}),
-				preview: precomputeRationalAngles({
-					n: a1.n,
-					d: a1.d,
-					b: a1.b
-				}),
-				base: a1.b,
-				usage: [
-					{
-						dimension: 'X',
-						angleFn: 'cos'
-					},
-					{
-						dimension: 'Y',
-						angleFn: 'sin'
-					},
-					{
-						dimension: 'Z',
-						angleFn: 'sin'
-					}
-				]
-			},
-			// The below is an example of what adding in a 3rd angle looks like
-			{
-				iterator: getRationalAngleIterator({
-					n: a2.n,
-					d: a2.d,
-					b: a2.b
-				}),
-				preview: precomputeRationalAngles({
-					n: a2.n,
-					d: a2.d,
-					b: a2.b
-				}),
+export const generateParams = (
+  a1: Rational,
+  a2: Rational,
[…]

### 2022-09-28 frontend/src/turtle_utils.ts

@@ -1,58 +1,67 @@
-import { Euler, Quaternion, Vector3 } from 'three';
-import type { Bounds, TurtlePath } from './interfaces';
+import { Euler, Quaternion, Vector3 } from "three";
+import type { Bounds, Rational, TurtlePath } from "./interfaces";
 
 const axis = new Vector3(0, 1, 0);
 
 const calculateCylinder = (p1: Vector3, p2: Vector3) => {
-	let length = p2.clone().sub(p1).length();
+  let length = p2.clone().sub(p1).length();
 
-	let diff = p1.clone().sub(p2);
-	let q = new Quaternion().setFromUnitVectors(axis, diff.normalize());
-	let rot = new Euler().setFromQuaternion(q);
+  let diff = p1.clone().sub(p2);
+  let q = new Quaternion().setFromUnitVectors(axis, diff.normalize());
+  let rot = new Euler().setFromQuaternion(q);
 
-	return {
-		position: p1.clone().add(p2).multiplyScalar(0.5),
-		scale: { y: length },
-		rotation: rot
-	};
+  return {
+    position: p1.clone().add(p2).multiplyScalar(0.5),
+    scale: { y: length },
+    rotation: rot,
+  };
 };
 
 // computes all cylinders
 export const computeCylinders = (path: TurtlePath) => {
-	let cylinders: any[] = [];
-	for (let i = 1; i < path.points.length; i++) {
-		let new_cylinder = calculateCylinder(path.points[i - 1], path.points[i]);
-		cylinders = [...cylinders, new_cylinder];
-	}
-	return cylinders;
+  let cylinders: any[] = [];
+  for (let i = 1; i < path.points.length; i++) {
+    let new_cylinder = calculateCylinder(path.points[i - 1], path.points[i]);
+    cylinders = [...cylinders, new_cylinder];
+  }
+  return cylinders;
 };
 
 // only computes cylinder for last point
 export const recomputeCylinders = (path: TurtlePath) => {
-	if (path.points.length == 1) return [];
+  if (path.points.length == 1) return [];
 
-	let new_cylinder = calculateCylinder(
-		path.points[path.points.length - 2],
-		path.points[path.points.length - 1]
-	);
-	// path.cylinders = [...path.cylinders, new_cylinder];
[…]

### 2022-09-28 frontend/src/near.ts
memo fracs

@@ -112,7 +112,8 @@ export const checkMinted = async (
   return response;
 };
 
-export const signIn = (near: Near) => {
+export const signIn = (near: Near, r1: Rational, r2: Rational) => {
+  setCurrentRationals(r1, r2, { n: 8, d: 9, b: 10 });
   getWalletConnection(near).requestSignIn({
     contractId: nearConfig.contractName,
   });

### 2022-09-28 frontend/src/turtle_utils.ts

@@ -57,11 +57,16 @@ export const getCentroid = (b: Bounds): Vector3 => {
   return v;
 };
 
-export const setCurrentRationals = (r1: Rational, r2: Rational, distance: Rational) => {
-  localStorage.setItem("rationals", JSON.stringify({ r1, r2 }));
+export const setCurrentRationals = (
+  r1: Rational,
+  r2: Rational,
+  distance: Rational
+) => {
+  localStorage.setItem("rationals", JSON.stringify({ r1, r2, distance }));
 };
 
 export const getCurrentRationals = () => {
-  if (!localStorage.getItem("rationals")) return undefined;
-  JSON.parse(localStorage.getItem("rationals"));
+  const rationals = window.localStorage.getItem("rationals");
+  if (!rationals) return undefined;
+  return JSON.parse(rationals);
 };

### 2022-09-28 frontend/src/near.ts
window state

@@ -101,6 +101,7 @@ export const getAllTokens = async (near): Promise<Token[]> => {
 };
 
 export const checkMinted = async (
+  near,
   r1: Rational,
   r2: Rational
 ): Promise<boolean> => {

### 2022-09-28 frontend/src/store.ts

@@ -7,6 +7,7 @@ import {
   precomputeRationalDistances,
   rationalFromStr,
 } from "./math/rationals";
+import { checkMinted } from "./near";
 import { getCurrentRationals } from "./turtle_utils";
 
 export type StoredParameters = {
@@ -108,7 +109,7 @@ export let controlParams: Writable<ControlParameters> = writable({
 });
 
 // Parse URL parameters to set a default for the parameters
-export const setParams = () => {
+export const setParams = async (near) => {
   try {
     const urlData = location.href.split("#")[1];
     const strs = urlData.split(";");
@@ -124,6 +125,9 @@ export const setParams = () => {
       };
     });
     parameters.set(generateParams(yaw, pitch, distance));
+    if (!(await checkMinted(near, yaw, pitch))) {
+      alert("No one has minted this shape! Feel free to mint it yourself");
+    }
   } catch (e) {
     if (getCurrentRationals()) {
       let { r1, r2, distance } = getCurrentRationals();
